I-CAH Blood Pressure Analysis

This file should be within your main directory of analysis. Within that directory should be a "bp_functions_folder" to store functions, and "bp_data_files_to_load" where files are saved and loaded. 

```{r, load software packages}
rm(list = ls())

#we first establish the location of the working directory where we keep everything, depending on whether it exists (i.e. which computer we are using)
#check C drive
if(file.exists("C:/Users/User/Documents/NRL_R_work/iCAH_Adiposity_Rebound")){
location_of_main_folder <-
  "C:/Users/User/Documents/NRL_R_work/iCAH_Adiposity_Rebound"
}

#take the working directory otherwise, which should work every time
if(!exists("location_of_main_folder")){
  location_of_main_folder <- getwd()
}

#paste the name of our functions folder into the path name
location_of_functions_folder <-
  paste0(location_of_main_folder, "/bp_functions_folder/")

#load the function that loads all the libraries and sources
source(paste0(location_of_functions_folder, "load_bp_libraries_and_sources_function.R"))

#paste together the location of the data files - we don't load in the first file, but we need this location for the end
location_of_data_files <-
  paste0(location_of_main_folder, "/bp_data_files_to_load/")

#run the function, pointing it towards the functions folder
load_bp_libraries_and_sources_function(
  location_of_functions_folder=location_of_functions_folder,
  location_of_data_files=location_of_data_files
)
```

```{r, read in files and write column names for reference}
bp_participants <- bp_participants_original <- 
  read.csv("./2021-12-01 Data extraction for ICAH BP study/STUDY ID 202107_NL BP CAH/STUDY DATASET CAH for BP study 202107_NL.csv", header=T, na.strings="")

write.csv(bp_participants_original, "bp_participants_original.csv")
```

```{r, create column names and missing data percentage files to refer to}
column_names_and_missing_percentages_bp_participants <-
  data.frame(
    Column=colnames(bp_participants),
    Percentage_complete=NA
  )

#create a loop to report the percentage complete
for (i in 1:length(column_names_and_missing_percentages_bp_participants$Column)){
  each_column <- column_names_and_missing_percentages_bp_participants[i,1]

  column_names_and_missing_percentages_bp_participants[i,"Percentage_complete"] <- 
    round(100*
      sum(!is.na(bp_participants[,c(each_column)])) / 
      length(bp_participants[,c(each_column)]), digits=1)
}

dir.create("Column_Names_and_missing_percentages")
write.csv(column_names_and_missing_percentages_bp_participants, 
          "./Column_Names_and_missing_percentages/colnames_and_missing_percentage_bp_participants.csv", 
          row.names=F)
```

########################################
Type of CAH
########################################

the non classic CAH response can go into another column that we call 'type_of_cah'. This can be created from 'Specify.the.actual.diagnosis...Details.of.Condition' which contains some information about salt wasters

```{r, creation of type_of_cah column and correction of type_of_cah from barcelona}
bp_participants$type_of_cah <- 
  bp_participants$Specify.the.actual.diagnosis...Details.of.Condition

#now we just correct for different spellings with grepl
bp_participants$type_of_cah <-
  ifelse(grepl(x=bp_participants$type_of_cah,
               pattern="Satwasting" , ignore.case = TRUE),
         "Salt_wasting",
         bp_participants$type_of_cah)

bp_participants$type_of_cah <-
  ifelse(grepl(x=bp_participants$type_of_cah,
               pattern="salt" , ignore.case = TRUE),
         "Salt_wasting",
         bp_participants$type_of_cah)

bp_participants$type_of_cah <-
  ifelse(grepl(x=bp_participants$type_of_cah,
               pattern="virilising" , ignore.case = TRUE),
         "Simple_virilising",
         bp_participants$type_of_cah)

bp_participants$type_of_cah <-
  ifelse(grepl(x=bp_participants$type_of_cah,
               pattern="late" , ignore.case = TRUE),
         "Non_classic",
         bp_participants$type_of_cah)

bp_participants$type_of_cah <-
  ifelse(grepl(x=bp_participants$type_of_cah,
               pattern="non-classic" , ignore.case = TRUE),
         "Non_classic",
         bp_participants$type_of_cah)

print("this frequency table shows the poor completion of this field:")

freq(bp_participants$type_of_cah)

```

############################################
Creation of manual correction columns and retention of original columns
############################################

Centres may be approached to manually correct outlying entries flagged as biologically or chronologically implausible

Original columns are retained 

```{r, creation of manually corrected columns for date, dob, height and weight and retention of original columns}
bp_participants$manually_corrected_longitudinal_date <- 
  bp_participants$Date...CAH.Longitudinal.Data

bp_participants$manually_corrected_dob <- 
  bp_participants$Date.of.birth...Birth

bp_participants$manually_corrected_height <- 
  bp_participants$Height..cm....CAH.Longitudinal.Data

bp_participants$manually_corrected_weight <- 
  bp_participants$Weight..kg....CAH.Longitudinal.Data

bp_participants$Date...CAH.Longitudinal.Data_original <- 
  bp_participants$Date...CAH.Longitudinal.Data

bp_participants$Date.of.birth...Birth_original <- 
  bp_participants$Date.of.birth...Birth

bp_participants$Height..cm....CAH.Longitudinal.Data_original <- 
  bp_participants$Height..cm....CAH.Longitudinal.Data

bp_participants$Weight..kg....CAH.Longitudinal.Data_original <- 
  bp_participants$Weight..kg....CAH.Longitudinal.Data

bp_participants$BMI...CAH.Longitudinal.Data_original <- 
  bp_participants$BMI...CAH.Longitudinal.Data
```

```{r, assessment of BMI in context of no data entry for height or weight}
#in order to learn anything from the data field BMI, we would need BMI without weight or BMI without height
bp_participants$bmi_without_weight <-
  ifelse(!is.na(bp_participants$BMI...CAH.Longitudinal.Data) &
           is.na(bp_participants$Weight..kg....CAH.Longitudinal.Data),
         1,
         0)
sum(bp_participants$bmi_without_weight)

bp_participants$bmi_without_height <-
  ifelse(!is.na(bp_participants$BMI...CAH.Longitudinal.Data) &
           is.na(bp_participants$Height..cm....CAH.Longitudinal.Data),
         1,
         0)
sum(bp_participants$bmi_without_height)

bp_participants_learn_from_bmi <-
  subset(bp_participants, 
         bmi_without_weight==1 | 
         bmi_without_height==1)

bp_participants_learn_from_bmi <-
  subset(bp_participants, 
         Register.ID...Record %in% bp_participants_learn_from_bmi$Register.ID...Record)

bp_participants_learn_from_bmi <- 
  bp_participants_learn_from_bmi[,c(
  "Register.ID...Record",
  "Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..",
  "manually_corrected_height",
  "Height..cm....CAH.Longitudinal.Data_original",
  "manually_corrected_weight",
  "Weight..kg....CAH.Longitudinal.Data_original",
  "BMI...CAH.Longitudinal.Data"
)]
```

```{r, back calculate height or weight from BMI if the former is missing}
#if we have BMI and weight but we don't have height, then back calculate height
bp_participants$manually_corrected_height <-
  ifelse(!is.na(bp_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(bp_participants$Weight..kg....CAH.Longitudinal.Data) &
          is.na(bp_participants$Height..cm....CAH.Longitudinal.Data),
         100*(bp_participants$Weight..kg....CAH.Longitudinal.Data /
          bp_participants$BMI...CAH.Longitudinal.Data)^0.5,
  bp_participants$manually_corrected_height)

#if we have BMI and height but we don't have weight, then back calculate weight
bp_participants$manually_corrected_weight <-
  ifelse(!is.na(bp_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(bp_participants$Height..cm....CAH.Longitudinal.Data) &
          is.na(bp_participants$Weight..kg....CAH.Longitudinal.Data),
         bp_participants$BMI...CAH.Longitudinal.Data *
          ((bp_participants$Height..cm....CAH.Longitudinal.Data/100)^2),
  bp_participants$manually_corrected_weight)

#tell me how many we back calculated height for
bp_participants$back_calculated_height <-
  ifelse(!is.na(bp_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(bp_participants$Weight..kg....CAH.Longitudinal.Data) &
          is.na(bp_participants$Height..cm....CAH.Longitudinal.Data),
         1,
  0)

sum(bp_participants$back_calculated_height)

#tell me how many we back calculated weight for
bp_participants$back_calculated_weight <-
  ifelse(!is.na(bp_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(bp_participants$Height..cm....CAH.Longitudinal.Data) &
          is.na(bp_participants$Weight..kg....CAH.Longitudinal.Data),
         1,
  0)

sum(bp_participants$back_calculated_weight)

view_back_calculated_weight <- 
  subset(bp_participants, back_calculated_weight==1)[,c(
  "Register.ID...Record",
  "Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..",
  "manually_corrected_height",
  "Height..cm....CAH.Longitudinal.Data_original",
  "manually_corrected_weight",
  "Weight..kg....CAH.Longitudinal.Data_original",
  "BMI...CAH.Longitudinal.Data"
)]

view_back_calculated_height <- 
  subset(bp_participants, back_calculated_height==1)[,c(
  "Register.ID...Record",
  "Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..",
  "manually_corrected_height",
  "Height..cm....CAH.Longitudinal.Data_original",
  "manually_corrected_weight",
  "Weight..kg....CAH.Longitudinal.Data_original",
  "BMI...CAH.Longitudinal.Data"
)]

ggplot(data=subset(bp_participants, back_calculated_weight==1)) +
  geom_point(aes(x=Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..,
                 y=manually_corrected_weight))

ggplot(data=subset(bp_participants, back_calculated_height==1)) +
  geom_point(aes(x=Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..,
                 y=manually_corrected_height))
```

############################################
Updated dates of birth sent by Glasgow 10/04/2024
############################################

```{r, manual update of dates of birth from data controller read in as a CSV file}
data_controller_update_2 <- 
  read.csv("./Other Data Extractions/202107_NL BP study - revised DoBs 10.4.24.csv")

bp_participants_with_update_2 <- 
  dplyr::left_join(bp_participants, 
                   data_controller_update_2, 
                   by=c("Register.ID...Record"="id_revised"))

print("check this number is zero to ensure no duplication at join:")
nrow(bp_participants) - nrow(bp_participants_with_update_2)

bp_participants <- bp_participants_with_update_2

bp_participants$manually_corrected_dob <- 
  ifelse(!is.na(bp_participants$dob_revised_10_04_2024), 
         bp_participants$dob_revised_10_04_2024, 
         bp_participants$manually_corrected_dob)

update_date_of_birth_frame_view <- 
  bp_participants[,c("dob_revised_10_04_2024",  
                     "Date.of.birth...Birth")]
```

```{r, further manual update of dates of birth following clarification from data controller}
data_controller_update_3 <- 
  read.csv(
    "./Other Data Extractions/DoB updates for new combined and rationalised list for NL.csv")

bp_participants_with_update_3 <- 
  dplyr::left_join(bp_participants, 
                   data_controller_update_3, 
                   by=c("Register.ID...Record"="id"))

print("check this number is zero to ensure no duplication at join:")
nrow(bp_participants) - nrow(bp_participants_with_update_3)

bp_participants <- 
  bp_participants_with_update_3

bp_participants$manually_corrected_dob <- 
  ifelse(!is.na(bp_participants$dob_revised_11_04_2024), 
         bp_participants$dob_revised_11_04_2024, 
         bp_participants$manually_corrected_dob)

revised_dates_of_birth_to_view <- 
  bp_participants[,c("dob_revised_11_04_2024",  
                     "Date.of.birth...Birth")]
```

############################################
Manual correction of dates of birth from centres by using previous extractions
############################################

```{r, manual update of dates of birth from data controller read in as a CSV file from 22042022}
data_controller_update_1 <- 
  read.csv("./Other Data Extractions/2022-04 Updated DOB from jillian.csv")

data_controller_update_1$Date.of.birth...Birth <- NULL

print("check these numbers are the same to ensure no duplication at join:")
nrow(bp_participants)

bp_participants_updated <- 
  dplyr::left_join(bp_participants, 
                   data_controller_update_1, 
                   by=c("Register.ID...Record"="id", 
                        "Centre.Name...Centre"="ï..Centre.Name...Centre"))

nrow(bp_participants_updated)

bp_participants <- 
  bp_participants_updated

bp_participants$manually_corrected_dob <- 
  ifelse(!is.na(bp_participants$DOB.in.registry..22.4.22.), 
                                                      bp_participants$DOB.in.registry..22.4.22., 
                                                      bp_participants$manually_corrected_dob)

bp_participants_updated_view <- 
  bp_participants[,c(
    "DOB.in.registry..22.4.22.",  
    "Date.of.birth...Birth")]
```

############################################
Adiposity rebound extraction dates of birth corrections
############################################

Further dates of birth update emailed over in February and March 2024

```{r, read and combine updated DOBs following adiposity rebound extraction}
#you shouldd directly reference the adiposity rebound extraction here, to prevent data duplication
further_corrected_dobs <- 
  read.csv("J:/External_cpu/R_work/iCAH_Adiposity_Rebound/Date_of_birth_responses/2024-03-04_Date_of_birth_responses.csv")

#join this in 
bp_participants_updated_2 <- 
  dplyr::left_join(bp_participants, 
                   further_corrected_dobs, 
                   by=c("Register.ID...Record"="id"))

print("This should be zero to ensure no duplication at join:")
nrow(bp_participants) -    
nrow(bp_participants_updated_2)                                   

bp_participants <- 
  bp_participants_updated_2

#then if we have an updated dob, we can make the manually_corrected_dob the updated one
bp_participants$manually_corrected_dob <- 
  ifelse(!is.na(bp_participants$ar_confirmed_date_of_birth), 
         bp_participants$ar_confirmed_date_of_birth, 
         bp_participants$manually_corrected_dob)
```

###################################
assessment of hypertension and antihypertensives columns
###################################

to flag people on antihypertensives, these columns were reviewed manually to ensure consistency and anyone who has any hint of treatment or diagnosis to be flagged

```{r, creation of manuallycorrected columns related to hypertension}
bp_participants$manually_corrected_hypertension_diagnosis_yes_no <-
  bp_participants$Hypertension...Comorbid.Conditions.and.Surgery

bp_participants$manually_corrected_hypertension_note <-
  bp_participants$Hypertension.note...Comorbid.Conditions.and.Surgery

bp_participants$manually_corrected_antihypertensives_yes_no <-
  bp_participants$Antihypertensives...Current.Medication

bp_participants$manually_corrected_antihypertensives_note <-
  bp_participants$Antihypertensives.note...Current.Medication
```

```{r, end of file so save all the listed dataframes into the parent directory}
save_bp_files_function(
  parent_directory = location_of_data_files,
  parent_file_name = "file_1")

Sys.time()
```
