Load packages and reread files using the prebuilt load files function

```{r, load packages}
rm(list = ls())

#we first establish the location of the working directory where we keep everything, depending on whether it exists (i.e. which computer we are using)
#check C drive
if(file.exists("C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure")){
location_of_main_folder <-
  "C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure"
}
#take the working directory otherwise, which should work every time?
if(!exists("location_of_main_folder")){
  location_of_main_folder <- 
    getwd()
}
#paste the name of our functions folder into the path name
location_of_functions_folder <-
  paste0(location_of_main_folder, "/bp_functions_folder/")

#load the function that loads all the libraries and sources
source(paste0(location_of_functions_folder, "load_bp_libraries_and_sources_function.R"))

#paste together the location of the data files - we don't load in the first file, but we need this location for the end
location_of_data_files <-
  paste0(location_of_main_folder, "/bp_data_files_to_load/")

#run the function, pointing it towards the functions folder
load_bp_libraries_and_sources_function(
  location_of_functions_folder=location_of_functions_folder,
  location_of_data_files=location_of_data_files
)

load_bp_files_function(previous_file_name = "file_21",
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("bp_data",
                                   #we take the number of imputations that we defined when running JOMO:
                                   "number_of_imputations"))

descr(bp_data$converted_17OHP_nmol_l_imputation_0)
```




https://www.peteredewitt.com/pedbp/

```{r, notes on how to use pedbp}
#install.packages("pedbp")
library(pedbp)

bp_cdf(age = 96, 
       male = 1, 
       sbp = 103, 
       dbp = 55)

flynn_chart_male <- 
  pedbp::bp_chart("sbp", male = 1, source = "flynn2017") + ylim(50,160) + xlim(0,240)
flynn_chart_male
flynn_chart_male_data <- flynn_chart_male$data
bp_chart("sbp", male = 1, source = "nhlbi") + ylim(50,160) + xlim(0,240)
bp_chart("sbp", male = 1, source = "gemelli1990") + ylim(50,160) + xlim(0,240)

x <- p_bp(q_sbp = 100, q_dbp = 60, age = 8, male = 0) 
x 
str(x)

p_bp(q_sbp = 95, # this is the entered systolic blood pressure
     q_dbp = 50, # this is the entered diastolic blood pressure
     male = 0, #0 here means female
     age = 28, #this is age IN MONTHS
     height = 92) # this is height in cm

p_bp(q_sbp = 95, q_dbp = 50, male = 0, age = 28, height = 92, source = "martin2022")  # Default
p_bp(q_sbp = 95, q_dbp = 50, male = 0, age = 28, height = 92, source = "gemelli1990")
p_bp(q_sbp = 95, q_dbp = 50, male = 0, age = 28, height = 92, source = "lo2013")
p_bp(q_sbp = 95, q_dbp = 50, male = 0, age = 28, height = 92, source = "nhlbi")
p_bp(q_sbp = 95, q_dbp = 50, male = 0, age = 28, height = 92, source = "flynn2017")

vignette("bp-distributions", package = "pedbp")

bp_data$sex_1_for_M_0_for_F <-
  ifelse(bp_data$sex_1_for_M_2_for_F==2,
         0,
         bp_data$sex_1_for_M_2_for_F)

  
bp_results <-
  p_bp(q_sbp = bp_data$Systolic..mmHg....CAH.Longitudinal.Data, 
       q_dbp = bp_data$Diastolic..mmHg....CAH.Longitudinal.Data, 
#       source = "gemelli1990", 
       male = 1, #doesn't work with bp_data$sex_1_for_M_0_for_F
       age = bp_data$age_to_use * 12, #age in months 
       height = bp_data$interpolated_height)
descr(bp_results$sbp_p)
descr(bp_results$dbp_p)
```

**************************
loop around each imputation to find blood pressure percentiles
**************************

I've redone this chunk to specify the normative centile reference data we are using, because we don't want to use the predefined hierarchy they have used within the package itself as it is so 'jagged' and stepped it doesn't make sense

```{r, calculate blood pressure percentiles for gemelli}
#it's unlikely or stupid if we impute these a different number of times, but I've written the code separately for the sake of it, we therefore need to take the smallest number of imputations to allow a loop to work for both systolic and diastolic together
number_of_imputations_for_systolic <-
#  max(bp_data$systolic_number_of_imputations, na.rm=T)
  number_of_imputations #I've rewritten this now just to take the predefined number of imputations

number_of_imputations_for_diastolic <-
#  max(bp_data$diastolic_number_of_imputations, na.rm=T)
  number_of_imputations #I've rewritten this now just to take the predefined number of imputations

#take the smallest number of imputations to facilitate the loop
number_of_imputations_for_bp <-
  ifelse(number_of_imputations_for_systolic < 
           number_of_imputations_for_diastolic,
         number_of_imputations_for_diastolic,
         number_of_imputations_for_systolic)

for (i in (0:number_of_imputations_for_bp)){
  #take out males and females as we have to run them through the app separately
  bp_data_male <- 
    subset(bp_data, Sex.at.birth...Birth=="Male")
  
  bp_data_fema <- 
    subset(bp_data, Sex.at.birth...Birth=="Female")
  
  bp_data_neither <- 
    subset(bp_data, Sex.at.birth...Birth!="Female" & Sex.at.birth...Birth!="Male")
  
  print(i)

  #take out the systolic and diastolic for each imputation
  systolic_column_frame_male <- 
    bp_data_male[,paste0("systolic_imputation_", i)]
  
  diastolic_column_frame_male <- 
    bp_data_male[,paste0("diastolic_imputation_", i)]

  systolic_column_frame_fema <- 
    bp_data_fema[,paste0("systolic_imputation_", i)]
  
  diastolic_column_frame_fema <- 
    bp_data_fema[,paste0("diastolic_imputation_", i)]

#run our app to find bp percentiles in males  
bp_percentile_frame_male_gemelli <-
  p_bp(q_sbp = systolic_column_frame_male[[1]], 
       q_dbp = diastolic_column_frame_male[[1]], 
       source = "gemelli1990", #if you don't specify source, it will use the appropriate hierarchy detailed on 
       male = 1, #doesn't work with bp_data$sex_1_for_M_0_for_F. male is 1, female is 0
       age = bp_data_male$age_to_use * 12, #age in months 
       height = bp_data_male$interpolated_height)

bp_percentile_frame_male_nhlbi <-
  p_bp(q_sbp = systolic_column_frame_male[[1]], 
       q_dbp = diastolic_column_frame_male[[1]], 
       source = "nhlbi", #if you don't specify source, it will use the appropriate hierarchy detailed on 
       male = 1, #doesn't work with bp_data$sex_1_for_M_0_for_F. male is 1, female is 0
       age = bp_data_male$age_to_use * 12, #age in months 
       height = bp_data_male$interpolated_height)

#run our app to find bp percentiles in femas  
bp_percentile_frame_fema_gemelli <-
  p_bp(q_sbp = systolic_column_frame_fema[[1]], 
       q_dbp = diastolic_column_frame_fema[[1]], 
       source = "gemelli1990", 
       male = 0, #doesn't work with bp_data$sex_1_for_M_0_for_F. male is 1, female is 0
       age = bp_data_fema$age_to_use * 12, #age in months
       height = bp_data_fema$interpolated_height)

bp_percentile_frame_fema_nhlbi <-
  p_bp(q_sbp = systolic_column_frame_fema[[1]], 
       q_dbp = diastolic_column_frame_fema[[1]], 
       source = "nhlbi", 
       male = 0, #doesn't work with bp_data$sex_1_for_M_0_for_F. male is 1, female is 0
       age = bp_data_fema$age_to_use * 12, #age in months
       height = bp_data_fema$interpolated_height)

#then we put the appropriate columns back into the frames

#put the male systolic in for gemelli
bp_data_male$new_column_percentile_gemelli <-
  bp_percentile_frame_male_gemelli$sbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_male$new_column_percentile_gemelli <-
  ifelse(bp_data_male$new_column_percentile_gemelli == 1, 
         0.9999999,
         bp_data_male$new_column_percentile_gemelli)
bp_data_male$new_column_percentile_gemelli <-
  ifelse(bp_data_male$new_column_percentile_gemelli == 0, 
         0.0000001,
         bp_data_male$new_column_percentile_gemelli)
#create z scores from percentiles using the r function qnorm for male systolic
bp_data_male$new_column_z_score_gemelli <- 
  qnorm(bp_data_male$new_column_percentile_gemelli)
descr(bp_data_male$new_column_z_score_gemelli)

#put the male systolic in for nhlbi
bp_data_male$new_column_percentile_nhlbi <-
  bp_percentile_frame_male_nhlbi$sbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_male$new_column_percentile_nhlbi <-
  ifelse(bp_data_male$new_column_percentile_nhlbi == 1, 
         0.9999999,
         bp_data_male$new_column_percentile_nhlbi)
bp_data_male$new_column_percentile_nhlbi <-
  ifelse(bp_data_male$new_column_percentile_nhlbi == 0, 
         0.0000001,
         bp_data_male$new_column_percentile_nhlbi)
#create z scores from percentiles using the r function qnorm for male systolic
bp_data_male$new_column_z_score_nhlbi <- 
  qnorm(bp_data_male$new_column_percentile_nhlbi)
descr(bp_data_male$new_column_z_score_nhlbi)

#use the percentile column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_male$new_column_percentile <-
  ifelse(bp_data_male$age_to_use < 1, 
         bp_data_male$new_column_percentile_gemelli,
         bp_data_male$new_column_percentile_nhlbi)

#use the z-score column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_male$new_column_z_score <-
  ifelse(bp_data_male$age_to_use < 1, 
         bp_data_male$new_column_z_score_gemelli,
         bp_data_male$new_column_z_score_nhlbi)

#rename our new column percentiles to contain the imputation number
names(bp_data_male)[names(bp_data_male)=="new_column_percentile"] <- 
  paste0("systolic_imp_centile_", i)
#rename our new column percentiles to contain the imputation number
names(bp_data_male)[names(bp_data_male)=="new_column_z_score"] <- 
  paste0("systolic_imp_z_score_", i)

#put the male diastolic in for gemelli
bp_data_male$new_column_percentile_gemelli <-
  bp_percentile_frame_male_gemelli$dbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_male$new_column_percentile_gemelli <-
  ifelse(bp_data_male$new_column_percentile_gemelli == 1, 
         0.9999999,
         bp_data_male$new_column_percentile_gemelli)
bp_data_male$new_column_percentile_gemelli <-
  ifelse(bp_data_male$new_column_percentile_gemelli == 0, 
         0.0000001,
         bp_data_male$new_column_percentile_gemelli)
#create z scores from percentiles using the r function qnorm for male diastolic
bp_data_male$new_column_z_score_gemelli <- 
  qnorm(bp_data_male$new_column_percentile_gemelli)
descr(bp_data_male$new_column_z_score_gemelli)

#put the male diastolic in for nhlbi
bp_data_male$new_column_percentile_nhlbi <-
  bp_percentile_frame_male_nhlbi$dbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_male$new_column_percentile_nhlbi <-
  ifelse(bp_data_male$new_column_percentile_nhlbi == 1, 
         0.9999999,
         bp_data_male$new_column_percentile_nhlbi)
bp_data_male$new_column_percentile_nhlbi <-
  ifelse(bp_data_male$new_column_percentile_nhlbi == 0, 
         0.0000001,
         bp_data_male$new_column_percentile_nhlbi)
#create z scores from percentiles using the r function qnorm for male diastolic
bp_data_male$new_column_z_score_nhlbi <- 
  qnorm(bp_data_male$new_column_percentile_nhlbi)
descr(bp_data_male$new_column_z_score_nhlbi)

#use the percentile column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_male$new_column_percentile <-
  ifelse(bp_data_male$age_to_use < 1, 
         bp_data_male$new_column_percentile_gemelli,
         bp_data_male$new_column_percentile_nhlbi)

#use the z-score column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_male$new_column_z_score <-
  ifelse(bp_data_male$age_to_use < 1, 
         bp_data_male$new_column_z_score_gemelli,
         bp_data_male$new_column_z_score_nhlbi)

#rename our new column percentiles to contain the imputation number
names(bp_data_male)[names(bp_data_male)=="new_column_percentile"] <- 
  paste0("diastolic_imp_centile_", i)
#rename our new column percentiles to contain the imputation number
names(bp_data_male)[names(bp_data_male)=="new_column_z_score"] <- 
  paste0("diastolic_imp_z_score_", i)


#put the fema systolic in for gemelli
bp_data_fema$new_column_percentile_gemelli <-
  bp_percentile_frame_fema_gemelli$sbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_fema$new_column_percentile_gemelli <-
  ifelse(bp_data_fema$new_column_percentile_gemelli == 1, 
         0.9999999,
         bp_data_fema$new_column_percentile_gemelli)
bp_data_fema$new_column_percentile_gemelli <-
  ifelse(bp_data_fema$new_column_percentile_gemelli == 0, 
         0.0000001,
         bp_data_fema$new_column_percentile_gemelli)
#create z scores from percentiles using the r function qnorm for fema systolic
bp_data_fema$new_column_z_score_gemelli <- 
  qnorm(bp_data_fema$new_column_percentile_gemelli)
descr(bp_data_fema$new_column_z_score_gemelli)

#put the fema systolic in for nhlbi
bp_data_fema$new_column_percentile_nhlbi <-
  bp_percentile_frame_fema_nhlbi$sbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_fema$new_column_percentile_nhlbi <-
  ifelse(bp_data_fema$new_column_percentile_nhlbi == 1, 
         0.9999999,
         bp_data_fema$new_column_percentile_nhlbi)
bp_data_fema$new_column_percentile_nhlbi <-
  ifelse(bp_data_fema$new_column_percentile_nhlbi == 0, 
         0.0000001,
         bp_data_fema$new_column_percentile_nhlbi)
#create z scores from percentiles using the r function qnorm for fema systolic
bp_data_fema$new_column_z_score_nhlbi <- 
  qnorm(bp_data_fema$new_column_percentile_nhlbi)
descr(bp_data_fema$new_column_z_score_nhlbi)

#use the percentile column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_fema$new_column_percentile <-
  ifelse(bp_data_fema$age_to_use < 1, 
         bp_data_fema$new_column_percentile_gemelli,
         bp_data_fema$new_column_percentile_nhlbi)

#use the z-score column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_fema$new_column_z_score <-
  ifelse(bp_data_fema$age_to_use < 1, 
         bp_data_fema$new_column_z_score_gemelli,
         bp_data_fema$new_column_z_score_nhlbi)

#rename our new column percentiles to contain the imputation number
names(bp_data_fema)[names(bp_data_fema)=="new_column_percentile"] <- 
  paste0("systolic_imp_centile_", i)
#rename our new column percentiles to contain the imputation number
names(bp_data_fema)[names(bp_data_fema)=="new_column_z_score"] <- 
  paste0("systolic_imp_z_score_", i)

#put the fema diastolic in for gemelli
bp_data_fema$new_column_percentile_gemelli <-
  bp_percentile_frame_fema_gemelli$dbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_fema$new_column_percentile_gemelli <-
  ifelse(bp_data_fema$new_column_percentile_gemelli == 1, 
         0.9999999,
         bp_data_fema$new_column_percentile_gemelli)
bp_data_fema$new_column_percentile_gemelli <-
  ifelse(bp_data_fema$new_column_percentile_gemelli == 0, 
         0.0000001,
         bp_data_fema$new_column_percentile_gemelli)
#create z scores from percentiles using the r function qnorm for fema diastolic
bp_data_fema$new_column_z_score_gemelli <- 
  qnorm(bp_data_fema$new_column_percentile_gemelli)
descr(bp_data_fema$new_column_z_score_gemelli)

#put the fema diastolic in for nhlbi
bp_data_fema$new_column_percentile_nhlbi <-
  bp_percentile_frame_fema_nhlbi$dbp_p
#correct any percentile that is exactly 1.000000 or 0.0000000 to prevent z scores that go to infinity
bp_data_fema$new_column_percentile_nhlbi <-
  ifelse(bp_data_fema$new_column_percentile_nhlbi == 1, 
         0.9999999,
         bp_data_fema$new_column_percentile_nhlbi)
bp_data_fema$new_column_percentile_nhlbi <-
  ifelse(bp_data_fema$new_column_percentile_nhlbi == 0, 
         0.0000001,
         bp_data_fema$new_column_percentile_nhlbi)
#create z scores from percentiles using the r function qnorm for fema diastolic
bp_data_fema$new_column_z_score_nhlbi <- 
  qnorm(bp_data_fema$new_column_percentile_nhlbi)
descr(bp_data_fema$new_column_z_score_nhlbi)

#use the percentile column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_fema$new_column_percentile <-
  ifelse(bp_data_fema$age_to_use < 1, 
         bp_data_fema$new_column_percentile_gemelli,
         bp_data_fema$new_column_percentile_nhlbi)

#use the z-score column from gemelli if we are under 1, from nhlbi if we are 1 or over
bp_data_fema$new_column_z_score <-
  ifelse(bp_data_fema$age_to_use < 1, 
         bp_data_fema$new_column_z_score_gemelli,
         bp_data_fema$new_column_z_score_nhlbi)

#rename our new column percentiles to contain the imputation number
names(bp_data_fema)[names(bp_data_fema)=="new_column_percentile"] <- 
  paste0("diastolic_imp_centile_", i)
#rename our new column percentiles to contain the imputation number
names(bp_data_fema)[names(bp_data_fema)=="new_column_z_score"] <- 
  paste0("diastolic_imp_z_score_", i)

#create dummy columns for those not male or female, just so we can bind appropriately

#put the neither systolic dummy columns in
bp_data_neither$new_column_percentile <-
  NA
bp_data_neither$new_column_z_score <-
  NA
#rename our new column percentiles to contain the imputation number
names(bp_data_neither)[names(bp_data_neither)=="new_column_percentile"] <- 
  paste0("systolic_imp_centile_", i)
#rename our new column z scores to contain the imputation number
names(bp_data_neither)[names(bp_data_neither)=="new_column_z_score"] <- 
  paste0("systolic_imp_z_score_", i)

#put the neither diastolic dummy columns in
bp_data_neither$new_column_percentile <-
  NA
bp_data_neither$new_column_z_score <-
  NA
#rename our new column
names(bp_data_neither)[names(bp_data_neither)=="new_column_percentile"] <- 
  paste0("diastolic_imp_centile_", i)
#rename our new column z scores to contain the imputation number
names(bp_data_neither)[names(bp_data_neither)=="new_column_z_score"] <- 
  paste0("diastolic_imp_z_score_", i)

#now bind our columns back
bp_data_both_male_and_female <-
  rbind(bp_data_male,
        bp_data_fema)

#recreate bp_data by binding those without sex also, which means we will now have the bp_data with the appropriate centiles
bp_data <-
  rbind(bp_data_both_male_and_female,
        bp_data_neither)

}

visual_check <-
  bp_data[,c(
    "age_to_use",
    "systolic_imputation_5",
    "systolic_imp_centile_5",
    "systolic_imp_z_score_5",
    "diastolic_imputation_5",
    "diastolic_imp_centile_5",
    "diastolic_imp_z_score_5"
  )]


```


```{r, this leaves us with the question}
print("How do we best calculate z scores or centiles of blood pressure for adults? NAHNES data?")
```

```{r, plotting dose of glucorticoids against age to help identify other preparations}
#for each centre we want a plot of absolute GC dose on age coloured by the GC type
descr(bp_data$absolute_daily_GC_dose_sum)
descr(bp_data$absolute_daily_GC_dose_sum_original)
dir.create("separate_centre_data")
for (each_centre in (unique(bp_data$Centre.Name...Centre))){
print(each_centre)
data_to_plot <-
  subset(bp_data, Centre.Name...Centre==each_centre)

#put a little clause in to render in black if there are no known daily preparations:
if(sum(is.na(data_to_plot$daily_preparation_of_GC_to_use_carried_to_use)) - length(data_to_plot$daily_preparation_of_GC_to_use_carried_to_use)<=0){

  centre_plot <- ggplot(data=data_to_plot, 
       aes(x=age_to_use,
           y=absolute_daily_GC_dose_sum)) +
  geom_point(colour="black") +
  themepowerpointlegend
  
}

#then render in colour if we have the preparations to use
if(sum(is.na(data_to_plot$daily_preparation_of_GC_to_use_carried_to_use)) - length(data_to_plot$daily_preparation_of_GC_to_use_carried_to_use)>0){

centre_plot <- ggplot(data=data_to_plot, 
       aes(x=age_to_use,
           y=absolute_daily_GC_dose_sum)) +
  geom_point(aes(colour=daily_preparation_of_GC_to_use_carried_to_use)) +
  themepowerpointlegend

}

ggsave(filename=paste0("centre_", each_centre, ".tif"), 
       path=paste0("separate_centre_data"),
       plot = centre_plot, 
       device="tiff",  
       width=10, 
       height=5, 
       compression = "lzw", 
       limitsize=F)

write.csv(x=data_to_plot, 
          file=paste0("separate_centre_data/data_for_centre_", each_centre, ".csv"),
          row.names=F)
}

print("Review the folder 'separate_centre_data' if you have any centres that have dosing as 'other' - this will give you a clue what they are in the plots, and allow you to look individually at the centre data to diagnose.")

```




```{r, end of file so save all the listed dataframes into the parent directory}
rm(number_of_imputations) #we only want to save this once and load it once

save_bp_files_function(
  parent_directory=location_of_data_files,
  parent_file="file_22")

Sys.time()
```

