
Load packages and reread files using the prebuilt load files function

```{r, load software packages}
rm(list = ls())

#we first establish the location of the working directory where we keep everything, depending on whether it exists (i.e. which computer we are using)
#check C drive
if(file.exists("C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure")){
location_of_main_folder <-
  "C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure"
}
#take the working directory otherwise, which should work every time?
if(!exists("location_of_main_folder")){
  location_of_main_folder <- 
    getwd()
}
#paste the name of our functions folder into the path name
location_of_functions_folder <-
  paste0(location_of_main_folder, "/bp_functions_folder/")

#load the function that loads all the libraries and sources
source(paste0(location_of_functions_folder, "load_bp_libraries_and_sources_function.R"))

#paste together the location of the data files - we don't load in the first file, but we need this location for the end
location_of_data_files <-
  paste0(location_of_main_folder, "/bp_data_files_to_load/")

#run the function, pointing it towards the functions folder
load_bp_libraries_and_sources_function(
  location_of_functions_folder=location_of_functions_folder,
  location_of_data_files=location_of_data_files
)

load_bp_files_function(previous_file_name = "file_10",
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("bp_data"))
```

We now have the file bp_data that has all of our data on one row per visit

***********************************
Summarising the Centres with data
************************************

We want to include all centre authors so let's print the centres

```{r, Summarising the Centres with data}
dir.create("codeprints")
write.csv(as.data.frame(freq(bp_data$Centre.Name...Centre)), 
          "codeprints/participatingcentres.csv")
```

```{r, load previous_extraction_20200311 and create appropriately named variables of interest}
previous_extraction_20200311 <- 
  read.csv("./bp_data_files_to_load/blank_previous_extraction.csv") #HERE YOU ADD ANY PREVIOUS EXTRACTION DATA FILE NAME TO INCORPORATE AGE INFORMATION

#create an appropriate id column
previous_extraction_20200311$id <- 
  as.integer(previous_extraction_20200311$Register.ID)

print("check we have the same number of integer id's as register ID's in the previous extraction frame - this number should be 0:")

length(unique(previous_extraction_20200311$id)) - 
  length(unique(previous_extraction_20200311$Register.ID))

#convert to numeric
previous_extraction_20200311$decimal_age_at_visit <-
  as.numeric(previous_extraction_20200311$Age.at.date.of.visit)

#convert visit to character to allow any manual adjustments after liaison with centres (using posix within ifelse causes problems)
previous_extraction_20200311$visit_date <- 
  as.character(previous_extraction_20200311$Date)
```

Here is where you would add any individual patient level adjustments from the previous extraction frame

```{r, convert visit date back to posix}
#then after our ifelse statements we convert to posixct
previous_extraction_20200311$visit_date <- 
  as.POSIXct(previous_extraction_20200311$visit_date, format="%Y-%m-%d")
```

```{r, turn decimal age into a number and process the date of birth in the previous extraction into R format}
previous_extraction_20200311$dob_calculated_from_decimal_age <- 
  previous_extraction_20200311$visit_date - 
  (as.numeric(previous_extraction_20200311$decimal_age_at_visit) * 60 * 60 * 24 * 365.25)

#this gives us a mixture of dates that are exact, and dates that have a time so we need to sort that out
previous_extraction_20200311$calculated_date_of_birth_character <- 
  as.character(previous_extraction_20200311$dob_calculated_from_decimal_age)

previous_extraction_20200311$calculated_date_of_birth_character <- 
  gsub(previous_extraction_20200311$calculated_date_of_birth_character, 
       pattern=" .*", 
       replacement="")

previous_extraction_20200311$calculated_date_of_birth_posix <-
  as.POSIXct(previous_extraction_20200311$calculated_date_of_birth_character)

previous_extraction_20200311$dob_calculated_from_decimal_age <- 
  previous_extraction_20200311$calculated_date_of_birth_posix 

#create id_visit_date to join our separate decimal ages as well

previous_extraction_20200311$id_visit_date <- 
  paste(previous_extraction_20200311$id , 
        previous_extraction_20200311$visit_date, sep="_")

previous_extraction_20200311$month_of_birth <- 
  format(as.Date(previous_extraction_20200311$visit_date, format="%Y-%m-%d"),
         "%m")

previous_extraction_20200311$day_of_birth <- 
  format(as.Date(previous_extraction_20200311$visit_date, format="%Y-%m-%d"),
         "%d")

previous_extraction_20200311$year_of_birth <- 
  format(as.Date(previous_extraction_20200311$visit_date, format="%Y-%m-%d"),
         "%Y")
```

```{r, calculate minimum and maximum date of births from decimal ages in previous_extraction_20200311}
previous_extraction_20200311_to_slice <- 
  previous_extraction_20200311[,c(
    "id", 
# you can have a look at the decimal ages here, but make sure you don't keep it in this frame as it will duplicate at join    
#    "decimal_age_at_visit",
    "dob_calculated_from_decimal_age")]

print("percentage of rows in previous extraction that have age recorded as NULL:")

subset(rownames_to_column(as.data.frame(freq(previous_extraction_20200311$decimal_age_at_visit))), 
       rowname=="NULL")$`% Valid`

a <- rownames_to_column(as.data.frame(freq(previous_extraction_20200311$decimal_age_at_visit)))
print("total rows in previous extraction that have age recorded as NULL or 'age' instead of a number:")
total_number_of_rows_without_age <-
  subset(rownames_to_column(as.data.frame(freq(previous_extraction_20200311$decimal_age_at_visit))), 
         rowname=="NULL")$`Freq` +
  subset(rownames_to_column(as.data.frame(freq(previous_extraction_20200311$decimal_age_at_visit))), 
         rowname=="age")$`Freq` +
  subset(rownames_to_column(as.data.frame(freq(previous_extraction_20200311$decimal_age_at_visit))), 
         rowname=="<NA>")$`Freq`

previous_extraction_20200311_to_slice <- 
  previous_extraction_20200311_to_slice[!is.na(previous_extraction_20200311_to_slice$dob_calculated_from_decimal_age),]

#total number of rows in the original extraction minus the rows without an age
nrow(previous_extraction_20200311) - 
  total_number_of_rows_without_age - 
  #should be the same as the total number of rows in the slice  
  nrow(previous_extraction_20200311_to_slice)

print("This number should be zero to show that we are trying to join all possible decimal ages that we have access to before the registry platform changed")

previous_extraction_dob_max_to_join <-
  previous_extraction_20200311_to_slice %>% 
  group_by(id) %>% 
  slice_max(dob_calculated_from_decimal_age, 
            n=1, 
            with_ties=F)

names(previous_extraction_dob_max_to_join)[
  names(previous_extraction_dob_max_to_join)=="dob_calculated_from_decimal_age"] <-
  "dob_calculated_from_decimal_age_max"

previous_extraction_dob_min_to_join <- 
  previous_extraction_20200311_to_slice %>% 
  group_by(id) %>% 
  slice_min(dob_calculated_from_decimal_age, n=1 , with_ties=F)

names(previous_extraction_dob_min_to_join)[
  names(previous_extraction_dob_min_to_join)=="dob_calculated_from_decimal_age"] <-
  "dob_calculated_from_decimal_age_min"

#join the minimum and maximum dates of birth together
previous_extraction_min_max_dob_to_join <- 
  dplyr::left_join(previous_extraction_dob_max_to_join,
                   previous_extraction_dob_min_to_join, 
                   by="id"  )

#calculate the range between minimum and maximum calculated dates of birth
previous_extraction_min_max_dob_to_join$range_of_previous_extraction_calculated_dates_of_birth <- 
  as.numeric(difftime(previous_extraction_min_max_dob_to_join$dob_calculated_from_decimal_age_max, 
                      previous_extraction_min_max_dob_to_join$dob_calculated_from_decimal_age_min, 
                      units="days"))/365.25


```

subset out the appropriate columns ready to join the necessary ages from the previous extraction

```{r, subset previous_extraction data ready to join}
#in order to join the previous_extraction data, we need it to have an ID and we need it to have an age at visit, and we need it to have a date of visit, so subset those out
previous_extraction_20200311_decimal_age_to_join <- 
  subset(previous_extraction_20200311, 
         !is.na(id) &
         !is.na(decimal_age_at_visit)  &
         !is.na(visit_date) & 
         decimal_age_at_visit!="NULL")

print("Number of visits from previous_extraction's final extraction that are available to join:")
nrow(previous_extraction_20200311_decimal_age_to_join)

#take out only the columns we want
previous_extraction_20200311_decimal_age_to_join <- 
  previous_extraction_20200311_decimal_age_to_join[,c(
    "id",
    "visit_date",
    "id_visit_date",
    "decimal_age_at_visit", 
    "dob_calculated_from_decimal_age"
    )]

#join in the minimum and maximum to that frame and make unique
previous_extraction_20200311_to_join <-
  unique(left_join(
    previous_extraction_20200311_decimal_age_to_join,
    previous_extraction_min_max_dob_to_join,
    by="id"))
  
nrow(previous_extraction_20200311_decimal_age_to_join)

print("was joined by")

nrow(previous_extraction_min_max_dob_to_join)

print("to create ")

nrow(previous_extraction_20200311_to_join)
```

```{r, take necessary columns from our recent extraction to join, as unique}
bp_dob_data_to_join <-
  unique(bp_data[,c(
    "id",
    "spurious_original_dob_code",
    "spurious_manually_corrected_dob_code",
    "manually_corrected_dob",
    "earliest_visit_date")])

print("check the number of rows with more than 1 ID, this should just be the total of the frequencies and therefore this number should be zero:")

nrow(subset(as.data.frame(freq(bp_dob_data_to_join$id)), Freq>1)) - 1

```

```{r, join the previous extraction to the bp_dob_data_to_join}
#we can left_join here because we dont have any decimal ages in bp_data, we are only learning from the decimal ages in the previous extraction

bp_previous_extraction_joined_to_model <-
  left_join(
    previous_extraction_20200311_to_join,
    bp_dob_data_to_join,
    by="id"
  )

print("this frame now has some id's that were in the previous extraction, which we don't have a manually_corrected_dob for becaues they weren't in the bp extraction. So in the case of NA in manually_corrected_dob, we instead insert the dob_calculated_from_decimal_age_min as it needs to be the same for each entry of 'id' for the modelling to work")

bp_previous_extraction_joined_to_model$manually_corrected_dob <-
  as.POSIXct(ifelse(is.na(bp_previous_extraction_joined_to_model$manually_corrected_dob),
         bp_previous_extraction_joined_to_model$dob_calculated_from_decimal_age_min,
         bp_previous_extraction_joined_to_model$manually_corrected_dob))

print("we also need to give these patients a spurious dob code of 1, because we dont have an official spurious dob for them")

bp_previous_extraction_joined_to_model$spurious_original_dob_code <-
  ifelse(is.na(bp_previous_extraction_joined_to_model$spurious_original_dob_code),
         1,
         bp_previous_extraction_joined_to_model$spurious_original_dob_code)

bp_previous_extraction_joined_to_model$spurious_manually_corrected_dob_code <-
  ifelse(is.na(bp_previous_extraction_joined_to_model$spurious_manually_corrected_dob_code),
         1,
         bp_previous_extraction_joined_to_model$spurious_manually_corrected_dob_code)

print("this is now the number of duplications of id_visit_date using the previous_extraction_20200311, because there must have been two data entries and the decimal age used was slightly different. This is okay to be duplicated in this case, because we can use those extra data points to model the possible date of birth, we just need to bear in mind in this frame id_visit_date isn't unique")

nrow(subset(as.data.frame(freq(bp_previous_extraction_joined_to_model$id_visit_date)), Freq>1))

print("create multiple_visits_from_previous_extraction_20200311 as a frame that shows the duplicate id_visit_dates but different decimal ages")

multiple_visits_from_previous_extraction_20200311 <- 
  subset(bp_previous_extraction_joined_to_model,
            id_visit_date %in%
            rownames(subset(as.data.frame(freq(bp_previous_extraction_joined_to_model$id_visit_date)), Freq>1)))
```


```{r, subset previous_extraction data ready to join}
print("you can look down the frame bp_previous_extraction_joined_to_model to check all the decimal ages are sensible numbers")

bp_previous_extraction_joined_to_model$decimal_age_at_visit <-
  as.numeric(bp_previous_extraction_joined_to_model$decimal_age_at_visit)
```

Can employ the earliest date to show some of the dates of birth are impossible

```{r, relate possible dates of birth to earliest visit date to establish any impossible dates of birth}
#establish the difference between the the minimum date of birth and the earliest visit date
bp_previous_extraction_joined_to_model$diff_time_calced_dob_min_more_than_earliest_visit_date <- 
  difftime(bp_previous_extraction_joined_to_model$dob_calculated_from_decimal_age_min,
           bp_previous_extraction_joined_to_model$earliest_visit_date)

bp_previous_extraction_joined_to_model$diff_time_calced_dob_max_more_than_earliest_visit_date <- 
  difftime(bp_previous_extraction_joined_to_model$dob_calculated_from_decimal_age_max,
           bp_previous_extraction_joined_to_model$earliest_visit_date)

bp_previous_extraction_joined_to_model$calculated_min_impos_as_post_1st_visit <- 
  ifelse(bp_previous_extraction_joined_to_model$diff_time_calced_dob_min_more_than_earliest_visit_date > 0, 
         1, 
         0)

print("number of visits where the calculated minimum dob is after the first visit, and therefore impossible:")
sum(bp_previous_extraction_joined_to_model$calculated_min_impos_as_post_1st_visit, na.rm=T)

#if the calculated_min dob is impossible, we change it to the earliest visit data
bp_previous_extraction_joined_to_model$dob_calculated_from_decimal_age_min <-
  as.POSIXct(ifelse(bp_previous_extraction_joined_to_model$calculated_min_impos_as_post_1st_visit==1,
         bp_previous_extraction_joined_to_model$earliest_visit_date,
         bp_previous_extraction_joined_to_model$dob_calculated_from_decimal_age_min))

bp_previous_extraction_joined_to_model$calculated_max_impos_as_post_1st_visit <- 
  ifelse(bp_previous_extraction_joined_to_model$diff_time_calced_dob_max_more_than_earliest_visit_date > 0, 
         1, 
         0)
print("number of visits where the calculated maximum dob is after the first visit, and therefore impossible:")
sum(bp_previous_extraction_joined_to_model$calculated_max_impos_as_post_1st_visit, na.rm=T)

#if the calculated_max dob is impossible, we change it to the earliest visit data
bp_previous_extraction_joined_to_model$dob_calculated_from_decimal_age_max <-
  as.POSIXct(ifelse(bp_previous_extraction_joined_to_model$calculated_max_impos_as_post_1st_visit==1,
         bp_previous_extraction_joined_to_model$earliest_visit_date,
         bp_previous_extraction_joined_to_model$dob_calculated_from_decimal_age_max))

print("look at calculated_dob_corrected_check_frame confirms the dates are still in date format")

calculated_dob_corrected_check_frame <- 
  bp_previous_extraction_joined_to_model[,c(
    "id", 
    "manually_corrected_dob", 
    "earliest_visit_date", 
    "dob_calculated_from_decimal_age_min", 
    "dob_calculated_from_decimal_age_max", 
    "calculated_min_impos_as_post_1st_visit", 
    "calculated_max_impos_as_post_1st_visit", 
    "diff_time_calced_dob_min_more_than_earliest_visit_date", 
    "diff_time_calced_dob_max_more_than_earliest_visit_date"
    )]

write.csv(calculated_dob_corrected_check_frame, 
          "calculated_dob_corrected_check_frame.csv")
```

that leaves us with bp_previous_extraction_joined_to_model

```{r, remove frames not necessary to save}
rm(previous_extraction_20200311_decimal_age_to_join)
```

```{r, end of file so save all the listed dataframes into the parent directory}
save_bp_files_function(
  parent_directory=location_of_data_files,
  parent_file="file_11")

Sys.time()
```


