Load packages and reread files using the prebuilt load files function

```{r, load software packages}
rm(list = ls())

#we first establish the location of the working directory where we keep everything, depending on whether it exists (i.e. which computer we are using)
#check C drive
if(file.exists("C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure")){
location_of_main_folder <-
  "C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure"
}
#take the working directory otherwise, which should work every time?
if(!exists("location_of_main_folder")){
  location_of_main_folder <- 
    getwd()
}
#paste the name of our functions folder into the path name
location_of_functions_folder <-
  paste0(location_of_main_folder, "/bp_functions_folder/")

#load the function that loads all the libraries and sources
source(paste0(location_of_functions_folder, "load_bp_libraries_and_sources_function.R"))

#paste together the location of the data files - we don't load in the first file, but we need this location for the end
location_of_data_files <-
  paste0(location_of_main_folder, "/bp_data_files_to_load/")

#run the function, pointing it towards the functions folder
load_bp_libraries_and_sources_function(
  location_of_functions_folder=location_of_functions_folder,
  location_of_data_files=location_of_data_files
)

load_bp_files_function(previous_file_name = "file_11",
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("bp_data",
                                   "bp_previous_extraction_joined_to_model"))
```

****************************************************************************************************************
calculating decimal age outliers and calculating average of decimal ages
****************************************************************************************************************

Making use of decimal ages. First we separate those with spurious date of birth, from those with a reliable date of birth

let's create difference_between_decimal_age_and_calculated_age_from_new_extraction_dob, which is age_at_visit_from_manually_corrected_dob minus the decimal age previously input.
Then we can visualise that within a facet plot

```{r, create difference_between_decimal_age_and_calculated_age_from_new_extraction_dob, the age_at_visit_from_manually_corrected_dob - decimal age previously input}
#create new calculated age from the dob we have from the new extraction
bp_previous_extraction_joined_to_model$age_at_visit_from_manually_corrected_dob <- 
  as.numeric(
    difftime(
      bp_previous_extraction_joined_to_model$visit_date, 
      bp_previous_extraction_joined_to_model$manually_corrected_dob,
      units="days")/
      365.25)

#calculate difference between the decimal age and the new calculated age
bp_previous_extraction_joined_to_model$difference_between_decimal_age_and_calculated_age_from_new_extraction_dob <- 
  bp_previous_extraction_joined_to_model$age_at_visit_from_manually_corrected_dob -
  as.numeric(bp_previous_extraction_joined_to_model$decimal_age_at_visit)

```

```{r, plot the difference_between_decimal_age_and_calculated_age_from_new_extraction_dob on decimal_age_at_visit }
dob_modelling_plot <- 
  ggplot(data=bp_previous_extraction_joined_to_model, 
         aes(x=decimal_age_at_visit, 
             y=difference_between_decimal_age_and_calculated_age_from_new_extraction_dob)) + 
  
  geom_point(size=0.1) +
  
  facet_wrap(~id) + 
  
  geom_smooth(method="lm", se=F) +  
  
  themenolegend + 
  
  coord_cartesian(ylim=c(-1.5, 1.5)) 

print("ungrey this to render the plot, rendering takes a long time at the size you need for it to be useful")
#ggsave(filename="dob_modelling_plot.tif", 
#       path=".", 
#       plot = dob_modelling_plot, device="tiff",  width=100, height=50, 
#       compression = "lzw", limitsize=F)
```

Method: 

draw a horizontal straight line through each patient

detect the standardised residuals from the straight line

remove outliers that have a standardised residual greater than 2.5 (this can be adjusted)

repeat that 4 times to make sure all outliers are removed

```{r, create a frame with the number of visits for each id}
#now we can take bp_previous_extraction_joined_to_model
number_of_visits_per_patient <- 
  subset(
    rownames_to_column(
    as.data.frame(freq(bp_previous_extraction_joined_to_model$id))), 
         rowname!= "Total" & 
           rowname!="<NA>")

number_of_visits_per_patient <- 
  data.frame(
    id=number_of_visits_per_patient$rowname,
    visits=number_of_visits_per_patient$Freq)
```

we have a number_of_visits_per_patient with the patients and the total number of visits they have

we want to loop round, fit the null model, flag any large standardised residuals and put that flag back into the frame

there are a lot of if statements in this loop to stop the iteration when we get down to one visit for each patient, because if you have one visit you obviously only have one age and you can't average between them.

```{r, loops of individual patient models of difference between decimal age and real DOB}
#set null frames to bind to
decimal_age_modelling_results <- NULL

decimal_age_is_an_outlier_frame_bound <- NULL
#define our residual threshold
residualthreshold <- 2.5

#skip this whole thing if we don't have previous data
if(length(number_of_visits_per_patient$id)>0){

for (patient in number_of_visits_per_patient$id){

individual_patient_frame_first_iteration <- 
  subset(bp_previous_extraction_joined_to_model, id==patient)
  
  #print the patient and number of visits to the console to review progress
  print(paste0("patient number: ", patient))
  
  print(paste0("number of visits: ", nrow(individual_patient_frame_first_iteration)))
  
  #you can't do this on people who only have one observation, so we use if to only do it if they have more than 1 row
  
  if (nrow(individual_patient_frame_first_iteration)>1) {
  
  #fit a linear model with flat sloped
  linear_model_first_iteration <- 
    lm(data=individual_patient_frame_first_iteration, 
          formula=difference_between_decimal_age_and_calculated_age_from_new_extraction_dob~1)
  
  #calculate the standardised residuals of the points and add them to the individual_patient_frame_first_iteration
  standard_res <- 
    individual_patient_frame_first_iteration$standard_res <-
    rstandard(linear_model_first_iteration)
  
  #create a data frame of the maximum and minimum standardised residuals
  standardised_residuals_of_dec_age_for_this_id <- 
    data.frame(
      id = patient,
               
      manually_corrected_dob = individual_patient_frame_first_iteration[1,"manually_corrected_dob"],
               
      spurious_original_dob_code = individual_patient_frame_first_iteration[1,"spurious_original_dob_code"],
               
      spurious_manually_corrected_dob_code =
        individual_patient_frame_first_iteration[1,"spurious_manually_corrected_dob_code"],
               
      n_visits_in_martin_frame = nrow(individual_patient_frame_first_iteration),
               
      max_stan_res_1st_iteration = max(standard_res),
               
      min_stan_res_1st_iteration = min(standard_res),
               
      range_stan_res_1st_iteration = max(standard_res)-min(standard_res)
               )
  }
  
  #create if there are no rows in the inidvidual_patient_frame then we can assign zero to the residuals, to ensure the patient has a row in the collected frame
  if (nrow(individual_patient_frame_first_iteration)<=1) {  
   standard_res <- 0   
    standardised_residuals_of_dec_age_for_this_id <- 
      data.frame(
        id=patient,
                 
        manually_corrected_dob = individual_patient_frame_first_iteration[1,"manually_corrected_dob"],
               
        spurious_original_dob_code = individual_patient_frame_first_iteration[1,"spurious_original_dob_code"],
        
        spurious_manually_corrected_dob_code =
          individual_patient_frame_first_iteration[1,"spurious_manually_corrected_dob_code"],
                 
        n_visits_in_martin_frame=nrow(individual_patient_frame_first_iteration),
                 
        min_stan_res_1st_iteration = 0,
                 
        max_stan_res_1st_iteration = 0,
                 
        range_stan_res_1st_iteration = 0
                 )
  }
  
  #subset out visits from the patient where the standardised residual is over threshold
  decimal_age_is_an_outlier_visits_1st_iteration <- 
    subset(individual_patient_frame_first_iteration, 
           standard_res > residualthreshold | 
           standard_res < -1*residualthreshold)
  
  #collect the id_visit_date and standard_res AND decimal_age_at_visit into a frame. Remember that in this frame, we don't necessarily have id_visit_date that is unique if multiple decimal_age_outlier are present, but we want to use them all and find out which ones are outliers / take the average of them
  
  if (nrow(decimal_age_is_an_outlier_visits_1st_iteration) > 0) {
    print("decimal age is an outlier in the 1st iteration")
  outlier_id_visits_1st_iteration <- 
    decimal_age_is_an_outlier_visits_1st_iteration[,c(
      "id_visit_date", 
      "spurious_original_dob_code",
      "spurious_manually_corrected_dob_code",
      "standard_res",
      "decimal_age_at_visit")]
  
  #add an iteration_removed column to this frame so we know at what iteration the value got removed
  outlier_id_visits_1st_iteration$iteration_removed <- 1
  }
  
  #create a null frame if this visit didn't result in any outliers, so we have something to join
  if (nrow(decimal_age_is_an_outlier_visits_1st_iteration) == 0) {
  outlier_id_visits_1st_iteration <- data.frame(NULL)
  }
  
  #collect the number of outliers at this 1st iteration that there are and add it to the standardised_residuals_of_dec_age_for_this_id frame
  standardised_residuals_of_dec_age_for_this_id$number_outlier_dec_ages_1st_iteration <-
    nrow(decimal_age_is_an_outlier_visits_1st_iteration)
  
  #then we do the same again having removed outliers as a second iteration. subset out the patient visits without the excessive standardised residuals
  individual_patient_frame_second_iteration <- 
    subset(individual_patient_frame_first_iteration, 
              standard_res < residualthreshold & 
              standard_res > -1*residualthreshold)
  
  if (nrow(individual_patient_frame_second_iteration) > 1){ 
    
  #fit the linear model again to remaining patients  
  linear_model_second_iteration <- 
    lm(data = individual_patient_frame_second_iteration, 
       formula = difference_between_decimal_age_and_calculated_age_from_new_extraction_dob ~ 1)  
  
  #calculate the standardised residuals again and add them to the frame
  standard_res <- 
    individual_patient_frame_second_iteration$standard_res <- 
    rstandard(linear_model_second_iteration)
  
  #calculate the minimum and maximum residueals to add to the frame
  standardised_residuals_of_dec_age_for_this_id$min_stan_res_2nd_iteration <- 
    min(standard_res)
  standardised_residuals_of_dec_age_for_this_id$max_stan_res_2nd_iteration <- 
    max(standard_res)
  standardised_residuals_of_dec_age_for_this_id$range_stan_res_2nd_iteration <- 
    max(standard_res)-min(standard_res)
  }
  
  if (nrow(individual_patient_frame_second_iteration) <= 1){
    
  standardised_residuals_of_dec_age_for_this_id$max_stan_res_2nd_iteration <- 0
  
  standardised_residuals_of_dec_age_for_this_id$min_stan_res_2nd_iteration <- 0
  
  standardised_residuals_of_dec_age_for_this_id$range_stan_res_2nd_iteration <- 0
  
  }   
  
  decimal_age_is_an_outlier_visits_2nd_iteration <- 
    subset(individual_patient_frame_second_iteration, 
           standard_res > residualthreshold | 
             standard_res < -1*residualthreshold)
  
  if (nrow(decimal_age_is_an_outlier_visits_2nd_iteration)>0){
  
  outlier_id_visits_2nd_iteration <- 
    decimal_age_is_an_outlier_visits_2nd_iteration[,c(
      "id_visit_date", 
      "spurious_original_dob_code",
      "spurious_manually_corrected_dob_code",
      "standard_res",
      "decimal_age_at_visit")]  
  
  outlier_id_visits_2nd_iteration$iteration_removed <- 
    2
  
  standardised_residuals_of_dec_age_for_this_id$number_outlier_dec_ages_2nd_iteration <- 
    nrow(outlier_id_visits_2nd_iteration)  
  
  }
  
  if (nrow(decimal_age_is_an_outlier_visits_2nd_iteration)==0){
  
    standardised_residuals_of_dec_age_for_this_id$number_outlier_dec_ages_2nd_iteration <- 0  
  
    outlier_id_visits_2nd_iteration <- data.frame(NULL)
    
  }
  
  #then we do the same again having removed outliers
  
  individual_patient_frame_third_iteration <- 
    subset(individual_patient_frame_second_iteration, 
           standard_res < residualthreshold & 
             standard_res > -1*residualthreshold)
  
  if (nrow(individual_patient_frame_third_iteration)>1){
    
  linear_model_third_iteration <- 
    lm(data = individual_patient_frame_third_iteration, 
                     formula = difference_between_decimal_age_and_calculated_age_from_new_extraction_dob ~ 1)  

  standard_res <-
    individual_patient_frame_third_iteration$standard_res <- rstandard(linear_model_third_iteration)
  
  standardised_residuals_of_dec_age_for_this_id$min_stan_res_3rd_iteration <- min(standard_res)
  
  standardised_residuals_of_dec_age_for_this_id$max_stan_res_3rd_iteration <- max(standard_res)
  
  standardised_residuals_of_dec_age_for_this_id$range_stan_res_3rd_iteration <- max(standard_res)-min(standard_res)
  
  }
  
  if (nrow(individual_patient_frame_third_iteration)<=1){
  
    standardised_residuals_of_dec_age_for_this_id$max_stan_res_3rd_iteration <- 0
  
    standardised_residuals_of_dec_age_for_this_id$min_stan_res_3rd_iteration <- 0
  
    standardised_residuals_of_dec_age_for_this_id$range_stan_res_3rd_iteration <- 0
    
  } 
  
  decimal_age_is_an_outlier_visits_3rd_iteration <- 
    subset(individual_patient_frame_third_iteration, 
           standard_res > residualthreshold | 
             standard_res < -1*residualthreshold)
  
  if (nrow(decimal_age_is_an_outlier_visits_3rd_iteration)>0){
  
  outlier_id_visits_3rd_iteration <- 
    decimal_age_is_an_outlier_visits_3rd_iteration[,c(
      "id_visit_date", 
      "spurious_original_dob_code",
      "spurious_manually_corrected_dob_code",
      "standard_res",
      "decimal_age_at_visit")]    
  
  outlier_id_visits_3rd_iteration$iteration_removed <- 3
  
  standardised_residuals_of_dec_age_for_this_id$number_outlier_dec_ages_3rd_iteration <- 
    nrow(outlier_id_visits_3rd_iteration)  
  
  }
  
  if (nrow(decimal_age_is_an_outlier_visits_3rd_iteration)==0){
  
    standardised_residuals_of_dec_age_for_this_id$number_outlier_dec_ages_3rd_iteration <- 0 
  
    outlier_id_visits_3rd_iteration <- data.frame(NULL)
  
    }
  
  #then we do the same again having removed outliers
  individual_patient_frame_fourth_iteration <- 
    subset(individual_patient_frame_third_iteration, 
           standard_res < residualthreshold & standard_res > -1*residualthreshold)
  
  nrow(individual_patient_frame_fourth_iteration)
  
  if (nrow(individual_patient_frame_fourth_iteration)>1){  
    
  linear_model_fourth_iteration <- lm(data = individual_patient_frame_fourth_iteration, 
                     formula = difference_between_decimal_age_and_calculated_age_from_new_extraction_dob ~ 1)  

  standard_res <- 
    individual_patient_frame_fourth_iteration$standard_res <-
    rstandard(linear_model_fourth_iteration)
  
  standardised_residuals_of_dec_age_for_this_id$min_stan_res_4th_iteration <- 
    min(standard_res)
  
  standardised_residuals_of_dec_age_for_this_id$max_stan_res_4th_iteration <- 
    max(standard_res)
  
  standardised_residuals_of_dec_age_for_this_id$range_stan_res_4th_iteration <- 
    max(standard_res) - min(standard_res)
  }
  
  if (nrow(individual_patient_frame_fourth_iteration)<=1){
    
  standardised_residuals_of_dec_age_for_this_id$min_stan_res_4th_iteration <- 0
  
  standardised_residuals_of_dec_age_for_this_id$max_stan_res_4th_iteration <- 0
  
  standardised_residuals_of_dec_age_for_this_id$range_stan_res_4th_iteration <- 0
  
  }  
  
  decimal_age_is_an_outlier_visits_4th_iteration <- 
    subset(individual_patient_frame_fourth_iteration, 
           standard_res > residualthreshold | 
             standard_res < -1*residualthreshold)
  
  if (nrow(decimal_age_is_an_outlier_visits_4th_iteration)>0){  
    
  outlier_id_visits_4th_iteration <- 
    decimal_age_is_an_outlier_visits_4th_iteration[,c(
      "id_visit_date", 
      "spurious_original_dob_code",
      "spurious_manually_corrected_dob_code",
      "standard_res",
      "decimal_age_at_visit")] 
  
  outlier_id_visits_4th_iteration$iteration_removed <- 4
  
  standardised_residuals_of_dec_age_for_this_id$number_outlier_dec_ages_4th_iteration <- 
    nrow(outlier_id_visits_4th_iteration)  
  
  }
  
  if (nrow(decimal_age_is_an_outlier_visits_4th_iteration)==0){
    
  standardised_residuals_of_dec_age_for_this_id$number_outlier_dec_ages_4th_iteration <- 
    0  
  
  outlier_id_visits_4th_iteration <- data.frame(NULL)
  
  }
  
#now we have linear_modelXXXiteration, ONLY if there were enough observations left following removal, otherwise we have to go back an iteration) with an intercept that is the average difference between the age_at_visit_from_manually_corrected_dob, and the decimal ages. We want to pull  out that intercept
  
  
  if (nrow(individual_patient_frame_fourth_iteration)>1){  
  standardised_residuals_of_dec_age_for_this_id$average_years_decimal_ages_over_manually_corrected_dob <- 
    coef(linear_model_fourth_iteration)["(Intercept)"]
  }

  if (nrow(individual_patient_frame_fourth_iteration)<=1){  
    if (nrow(individual_patient_frame_third_iteration)>1){
    standardised_residuals_of_dec_age_for_this_id$average_years_decimal_ages_over_manually_corrected_dob <- 
      coef(linear_model_third_iteration)["(Intercept)"]
    }
    
    if (nrow(individual_patient_frame_third_iteration)<=1){  
      if (nrow(individual_patient_frame_second_iteration)>1){
      standardised_residuals_of_dec_age_for_this_id$average_years_decimal_ages_over_manually_corrected_dob <- 
        coef(linear_model_second_iteration)["(Intercept)"]
      }
      
      if (nrow(individual_patient_frame_second_iteration)<=1){
        if (nrow(individual_patient_frame_first_iteration)>1){
        standardised_residuals_of_dec_age_for_this_id$average_years_decimal_ages_over_manually_corrected_dob <- 
          coef(linear_model_first_iteration)["(Intercept)"]
        }
        
        if (nrow(individual_patient_frame_first_iteration)<=1){
          standardised_residuals_of_dec_age_for_this_id$average_years_decimal_ages_over_manually_corrected_dob <- 0
}}}}
  
#we then bind all the iteration frames to collect results
  
#collect all the id_visit_dates that had outliers that we removed, and the residual values that got them removed

nrow(outlier_id_visits_4th_iteration)

outlier_id_visits <- rbind(
  outlier_id_visits_1st_iteration,
  outlier_id_visits_2nd_iteration,
  outlier_id_visits_3rd_iteration,
  outlier_id_visits_4th_iteration
  )

decimal_age_modelling_results <- 
  rbind(decimal_age_modelling_results, 
        standardised_residuals_of_dec_age_for_this_id)

decimal_age_is_an_outlier_frame_bound <- 
  rbind(decimal_age_is_an_outlier_frame_bound, 
        outlier_id_visits)  
}

}
print("following this loop we have the frame decimal_age_modelling_results which has one row for each id, and then a column with number_outlier_dec_ages_1st_iteration and so on for 2nd 3rd and 4th iterations. It also has the standardised residuals for each that were removed. We also have decimal_age_is_an_outlier_frame_bound which tells us specifically which id_visit_date and decimal_age_at_visit was declared an outlier.")

```

we now have, for each patient, an impression of how many decimal ages were outliers, and a list of these id_visit_dates within decimal_age_is_an_outlier_frame_bound. we can therefore join these into the main frame to tell us the methodology behind the calculation of the age at each visit

```{r, calculate modelling_corrected_dob and total number of outliers removed}
#skip this whole thing if we don't have previous data
if(length(number_of_visits_per_patient$id)>0){
  
  #we have a number of years that the decimal ages are consistently over the manually_corrected_dob average_years_decimal_ages_over_manually_corrected_dob . Therefore the modelling_corrected_dob should be the manually_corrected_dob + average_years_decimal_ages_over_manually_corrected_dob
decimal_age_modelling_results$average_days_decimal_ages_over_manually_corrected_dob <-
  as.integer(
    decimal_age_modelling_results$average_years_decimal_ages_over_manually_corrected_dob * 
      365.25)

#to do this we want to use lubridate and add a number of days
decimal_age_modelling_results$modelling_corrected_dob <-
  as.Date(decimal_age_modelling_results$manually_corrected_dob) +
  decimal_age_modelling_results$average_days_decimal_ages_over_manually_corrected_dob

decimal_age_modelling_results$total_decimal_age_is_an_outliers_removed <- 
  decimal_age_modelling_results$number_outlier_dec_ages_1st_iteration +
  decimal_age_modelling_results$number_outlier_dec_ages_2nd_iteration +
  decimal_age_modelling_results$number_outlier_dec_ages_3rd_iteration +
  decimal_age_modelling_results$number_outlier_dec_ages_4th_iteration

print("decimal_age_modelling_results_residual_threshold_ with the residual threshold appended is printed to csv to help assess different residual thresholds")

write.csv(
  decimal_age_modelling_results, 
  paste0("decimal_age_modelling_results_from_residual_threshold_", 
  residualthreshold, 
  ".csv"),
  row.names = F)  


print("ids that have a large difference_between_decimal_age_and_calculated_age_from_new_extraction_dob of over 1 or less than -1 to review in the original extraction spreadsheet. If this is done incorporate any manual changes into file 9")

outlying_patients_in_martin_frame_to_manually_review <-
  unique(subset(decimal_age_modelling_results, 
       average_years_decimal_ages_over_manually_corrected_dob> 1 | 
       average_years_decimal_ages_over_manually_corrected_dob < -1)$id)
outlying_patients_in_martin_frame_to_manually_review

previous_extraction <- 
  read.csv("./bp_data_files_to_load/blank_previous_extraction.csv")

previous_extraction_to_review <-
  subset(
    previous_extraction, 
    Register.ID %in% outlying_patients_in_martin_frame_to_manually_review)

previous_extraction_to_review <-
  unique(previous_extraction_to_review[,c(
    "Register.ID",
    "Date.of.Birth",
    "Date",
    "Age.at.date.of.visit")])

write.csv(previous_extraction_to_review, 
          "previous_extraction_to_review.csv", 
          row.names = F)
}
```

```{r, check our modelled dates of birth against the non_spurious dates of birth that we have access to}
#skip this whole thing if we don't have previous data
if(length(number_of_visits_per_patient$id)>0){
  
decimal_age_modelling_results_to_view <-
  decimal_age_modelling_results[,c(
    "id",
    "n_visits_in_martin_frame",
    "total_decimal_age_is_an_outliers_removed",
    "spurious_original_dob_code",
    "spurious_manually_corrected_dob_code",
    "manually_corrected_dob",
    "modelling_corrected_dob",
    "average_years_decimal_ages_over_manually_corrected_dob")]

print("we can therefore describe the correction factor in those WITHOUT a spurious DOB, to check the methdology. This should be an average of zero correction because we have a reliable date of birth. There then only remains the question of whether you trust the modelling age MORE than the non spurious date of birth, because there are more entries of data that back it up, rather than a non spurious date of birth which is only entered once. I decide not to take this, but should review these patients' dates of birth when contacting centres.")

a <- subset(decimal_age_modelling_results_to_view,
             spurious_manually_corrected_dob_code==0)
descr(a$average_years_decimal_ages_over_manually_corrected_dob)

a <- subset(decimal_age_modelling_results_to_view,
             spurious_original_dob_code==0)
descr(a$average_years_decimal_ages_over_manually_corrected_dob)

print("take out the patients that have a reliable date of birth, but have a large difference with a modelled date of birth, and n_visits_in_martin_frame of more than 4 (which means the date of birth modelling is more reliable")

decimal_age_modelling_results_may_be_better_than_non_spurious <-
  subset(decimal_age_modelling_results_to_view,
         n_visits_in_martin_frame>4 &
         average_years_decimal_ages_over_manually_corrected_dob > 0.1 &
         spurious_manually_corrected_dob_code==0   |
         n_visits_in_martin_frame>4 &
         average_years_decimal_ages_over_manually_corrected_dob < -0.1 &
         spurious_manually_corrected_dob_code==0 )

print("the list of patients to review when contacting centres flagged by this methodology is:")
decimal_age_modelling_results_may_be_better_than_non_spurious$id

}
```

We now have all the information for modelled dates of birth within decimal_age_modelling_results frame. 

HOWEVER - these modelled dates of birth may be earlier than the earliest visit. in which case we make a correction for the earliest visit in that frame when we employ the following hierarchy:

If we have a non spurious date of birth, then we use manually_corrected_dob

If we have a spurious date of birth, then we use modelling_corrected_dob

We can now join to our bp_data file

```{r, join dob modelled from decimal age}
#skip this whole thing if we don't have previous data
if(length(number_of_visits_per_patient$id)>0){
decimal_age_modelling_results_to_join <-
  decimal_age_modelling_results[,c(
    "id",
    "n_visits_in_martin_frame",
    "total_decimal_age_is_an_outliers_removed",
    "modelling_corrected_dob",
    "average_years_decimal_ages_over_manually_corrected_dob")]
}
#if we don't have previous data then we just create a previous frame with empty columns
#skip this whole thing if we don't have previous data
if(length(number_of_visits_per_patient$id)==0){
decimal_age_modelling_results_to_join <-
  data.frame(
    id=integer(0),
    n_visits_in_martin_frame=numeric(0),
    total_decimal_age_is_an_outliers_removed=numeric(0),
    modelling_corrected_dob=POSIXct(0),
    average_years_decimal_ages_over_manually_corrected_dob=numeric(0))
}
#turn the id into an integer just so it's okay to join
decimal_age_modelling_results_to_join$id <- 
  as.integer(decimal_age_modelling_results_to_join$id)


bp_data_with_modelling_corrected_dob <-
  left_join(bp_data,
            decimal_age_modelling_results_to_join,
            by="id")

```


```{r, adjust modelling_corrected_dob for earliest_visit_date}
#we have modelled the average date of birth, but we haven't corrected for the absolute minimum date of birth which is the earliest visit date. We could do that within the martin frame and modelling, but instead we can do it here in the overall data frame
those_with_corrected_first_visit_modelled_dob <-
  subset(bp_data_with_modelling_corrected_dob,
         modelling_corrected_dob > earliest_visit_date)

print("Bear in mind, this is all patients that have a modelled dob later than their first visit date. Not necessarily all these patients will have their modelled dob used")
unique(those_with_corrected_first_visit_modelled_dob$id)

bp_data_with_modelling_corrected_dob$modelling_corrected_dob <-
  ifelse(
    bp_data_with_modelling_corrected_dob$earliest_visit_date < 
      bp_data_with_modelling_corrected_dob$modelling_corrected_dob,
    as.character(bp_data_with_modelling_corrected_dob$earliest_visit_date),
    as.character(bp_data_with_modelling_corrected_dob$modelling_corrected_dob)
  )

str(bp_data_with_modelling_corrected_dob$modelling_corrected_dob)
```


```{r, check the join isnt duplicating rows}
print("original frame had this many rows:")
nrow(bp_data)

print("I joined this many rows:")
nrow(decimal_age_modelling_results_to_join)

print("This should say zero to prove I haven't duplicated rows")
nrow(bp_data_with_modelling_corrected_dob) - nrow(bp_data)

#then I can rationalise the data frame name
bp_data <- 
  bp_data_with_modelling_corrected_dob
```

```{r, summary of the number of decimal age outliers removed}
print("Total number of visits from bp_data with a decimal age from the martin extraction")
sum(
  !is.na(
    subset(bp_data, spurious_manually_corrected_dob_code==1)$
      n_visits_in_martin_frame))

#extract one row for each patient from our final frame, to find out the total number of outliers we removed
bp_data_summary_of_martin_data_that_was_joined <-
  unique(bp_data[,c(
    "id",
    "n_visits_in_martin_frame",
    "total_decimal_age_is_an_outliers_removed",
    "spurious_manually_corrected_dob_code",
    "modelling_corrected_dob",
    "average_years_decimal_ages_over_manually_corrected_dob")])

print("Total number of visits with a decimal age that was removed in patients that had a spurious manually corrected date of birth")

print(sum(!is.na(subset(bp_data_summary_of_martin_data_that_was_joined,
                  spurious_manually_corrected_dob_code==1)$total_decimal_age_is_an_outliers_removed)))
```

```{r, check spuriosity}
#freq(bp_data$manually_corrected_dob)
freq(bp_data$spurious_manually_corrected_dob_code)
freq(bp_data$spurious_original_dob_code)
```

That will then leave us with some patients where we didn't have decimal ages and still have a spurious dob. For these patients we will need to create midpoint_corrected_dob. We do that in the next file.

```{r, end of file so save all the listed dataframes into the parent directory}
save_bp_files_function(
  parent_directory=location_of_data_files,
  parent_file="file_12")
Sys.time()
```


