This frame conducts last observation carried forward and next observation carried backward.

PLEASE NOTE - your data should have unique id_visit_dates. If this is not the case the code in chunk 2 will arbitrarily chop the data to the largest age at an id_visit_date. Please assess your data manually if this occurs.

```{r, load software packages}
rm(list = ls())

#we first establish the location of the working directory where we keep everything, depending on whether it exists (i.e. which computer we are using)
#check C drive
if(file.exists("C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure")){
location_of_main_folder <-
  "C:/Users/User/Documents/NRL_R_work/iCAH_Blood_pressure"
}
#take the working directory otherwise, which should work every time?
if(!exists("location_of_main_folder")){
  location_of_main_folder <- 
    getwd()
}
#paste the name of our functions folder into the path name
location_of_functions_folder <-
  paste0(location_of_main_folder, "/bp_functions_folder/")

#load the function that loads all the libraries and sources
source(paste0(location_of_functions_folder, "load_bp_libraries_and_sources_function.R"))

#paste together the location of the data files - we don't load in the first file, but we need this location for the end
location_of_data_files <-
  paste0(location_of_main_folder, "/bp_data_files_to_load/")

#run the function, pointing it towards the functions folder
load_bp_libraries_and_sources_function(
  location_of_functions_folder=location_of_functions_folder,
  location_of_data_files=location_of_data_files
)

load_bp_files_function(previous_file_name = "file_14",
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("bp_data"))
```
```{r}
#add a clause for multiple id_visit_dates that throws a warning and ensures individual id_visit_dates
if(length(unique(bp_data$id_visit_date)) < nrow(bp_data)){
  print("Alert! Alert! You have duplicated id_visit_dates. Please assess your data and find the multiple id_visit_dates and correct this error manually. For now this function obruptly strips the data down to a single id_visit_date arbitrarily.")
  bp_data <-
    bp_data %>%
    group_by(id_visit_date) %>%
    slice_max(age_to_use, n=1, with_ties = F)
}
```


************
correct fludro dose before carrying for the column saying yes no or not known
***************

```{r, correct inappropriate carry forwards of Not known for fludrocortisone - do this for all patients}
#if a patient has actively declared 'Not known' for whether they are taking GC, then they shouldn't have dose information
#before we do a blanket correction here, we should record how many this applies to 
print("This is the number of not knowns we have registered in the file.")
freq(bp_data$Fludrocortisone...Current.Medication)

bp_data_FC_not_known <-
  subset(bp_data, Fludrocortisone...Current.Medication=="Not known")
```

```{r, correct inappropriate does of Not known for fludrocortisone}
#if they are declared not known to be taking fludrocortisone, then there dose must be recorded as not known
bp_data$total_daily_fludro_dose <-
    ifelse(bp_data$Fludrocortisone...Current.Medication=="Not known",
           NA,
           bp_data$total_daily_fludro_dose)
```


************************************
Accounting for patients not taking fludrocortisone
************************************

As we discovered the perpetual nature of fields that disappear from the users view when they select 'No' for a drug, we know that we should give hierarchical preference to when a patient is not taking fludrocortisone and not takine salt

```{r, Impute zero fludro dose for all those with No for Fludrocortisone...Current.Medication_carried_to_use }
bp_data$total_daily_fludro_dose_with_zero <-
  bp_data$total_daily_fludro_dose

bp_data$total_daily_fludro_dose_with_zero <-
  ifelse(bp_data$Fludrocortisone...Current.Medication=="No", 
  0, 
  bp_data$total_daily_fludro_dose_with_zero)

```

```{r, correct inappropriate doses of Not known for salt - do this for all patients}
bp_data$converted_salt_mass <-
    ifelse(bp_data$Salt.replacement...Current.Medication=="Not known",
           NA,
           bp_data$converted_salt_mass)
  
  bp_data$converted_salt_per_kg_or_absolute <-
    ifelse(bp_data$Salt.replacement...Current.Medication=="Not known",
           NA,
           bp_data$converted_salt_per_kg_or_absolute)
```

```{r, Impute zero salt dose for all those with No for Salt.replacement...Current.Medication}
bp_data$converted_salt_mass_with_zero <-
  bp_data$converted_salt_mass

bp_data$converted_salt_mass_with_zero <-
  ifelse(bp_data$Salt.replacement...Current.Medication=="No", 
  0, 
  bp_data$converted_salt_mass_with_zero)

```

After file with manual corrections from glucocorticoid notes, we can now trust the value of Glucocorticoids...Current.Medication . If it states Yes, we are happy they are on treatment. If it states No, we are happy they are not on treatment. If it states Not known, then we don't know. There will be values of NA

We now want to use last observation carried forward from the zoo package to carry observations forward

```{r, start by establishing maximum limits for LOCF. this is best done by creating another column that we can adjust depending on other columns. This way we can add extra riders into these clauses that allow us to not carry forward if we have reason not to in another column}
#for those under 1 year, the maximum is:
bp_data$maximum_years_LOCF <-
  ifelse(
    bp_data$age_to_use < 1,
    0.5,
    NA
  )
#for those under 3 years, the maximum is:
bp_data$maximum_years_LOCF <-
  ifelse(
    bp_data$age_to_use >= 1 &
    bp_data$age_to_use < 3 ,
    1,
    bp_data$maximum_years_LOCF
  )
#for those under 5 years, the maximum is:
bp_data$maximum_years_LOCF <-
  ifelse(
    bp_data$age_to_use >= 3 &
    bp_data$age_to_use < 5 ,
    2,
    bp_data$maximum_years_LOCF
  )
#for those under 10 years, the maximum is:
bp_data$maximum_years_LOCF <-
  ifelse(
    bp_data$age_to_use >= 5 &
    bp_data$age_to_use < 10 ,
    3,
    bp_data$maximum_years_LOCF
  )
#for those under 15 years, the maximum is:
bp_data$maximum_years_LOCF <-
  ifelse(
    bp_data$age_to_use >= 10 &
    bp_data$age_to_use < 15 ,
    4,
    bp_data$maximum_years_LOCF
  )
#for those under 20 years, the maximum is:
bp_data$maximum_years_LOCF <-
  ifelse(
    bp_data$age_to_use >= 15 &
    bp_data$age_to_use < 20 ,
    5,
    bp_data$maximum_years_LOCF
  )
#for those over 20 years, the maximum is:
bp_data$maximum_years_LOCF <-
  ifelse(
    bp_data$age_to_use >= 20 &
    bp_data$age_to_use < 80 ,
    10,
    bp_data$maximum_years_LOCF
  )

  
```

```{r, also establish maximum limits for NOCB. this is best done by creating another column that we can adjust depending on other columns. This way we can add extra riders into these clauses that allow us to not carry forward if we have reason not to in another column}
#for those under 1 year, the maximum is:
bp_data$maximum_years_NOCB <-
  ifelse(
    bp_data$age_to_use < 1,
    0.5,
    NA
  )
#for those under 3 years, the maximum is:
bp_data$maximum_years_NOCB <-
  ifelse(
    bp_data$age_to_use >= 1 &
    bp_data$age_to_use < 3 ,
    1,
    bp_data$maximum_years_NOCB
  )
#for those under 5 years, the maximum is:
bp_data$maximum_years_NOCB <-
  ifelse(
    bp_data$age_to_use >= 3 &
    bp_data$age_to_use < 5 ,
    2,
    bp_data$maximum_years_NOCB
  )
#for those under 10 years, the maximum is:
bp_data$maximum_years_NOCB <-
  ifelse(
    bp_data$age_to_use >= 5 &
    bp_data$age_to_use < 10 ,
    3,
    bp_data$maximum_years_NOCB
  )
#for those under 15 years, the maximum is:
bp_data$maximum_years_NOCB <-
  ifelse(
    bp_data$age_to_use >= 10 &
    bp_data$age_to_use < 15 ,
    4,
    bp_data$maximum_years_NOCB
  )
#for those under 20 years, the maximum is:
bp_data$maximum_years_NOCB <-
  ifelse(
    bp_data$age_to_use >= 15 &
    bp_data$age_to_use < 20 ,
    5,
    bp_data$maximum_years_NOCB
  )
#for those over 20 years, the maximum is:
bp_data$maximum_years_NOCB <-
  ifelse(
    bp_data$age_to_use >= 20 &
    bp_data$age_to_use < 80 ,
    10,
    bp_data$maximum_years_NOCB
  )


```

```{r, create a frame of the visit date of every piece of data, retaining id and id_visit_date as previous}
#before we carry anything forward, we want a visit date for all data. Then we will be able to use last observation carried forward for these visit dates, to find out where any last observation carried forward data has come from
bp_data_visit_dates_of_data <-
  bp_data

#loop around every column taking the visit date if there is data in the cell
for (i in (1:ncol(bp_data_visit_dates_of_data))){
bp_data_visit_dates_of_data[i] <- 
  ifelse(is.na(bp_data_visit_dates_of_data[[i]]), 
         NA, 
         (bp_data_visit_dates_of_data$visit_date_unix))

#as we've used ifelse, we have to convert back from UNIX
bp_data_visit_dates_of_data[[i]] <- 
  as.POSIXct(bp_data_visit_dates_of_data[[i]] , origin="1970-01-01")
}

#however, we don't want the date of the id, or the id visit_date, so we remove them
bp_data_visit_dates_of_data$id <- NULL
bp_data_visit_dates_of_data$id_visit_date <- NULL

#then bind the original columns back in 
id_column <- data.frame(id=bp_data$id)
id_visit_date_column <- data.frame(id_visit_date=bp_data$id_visit_date)
bp_data_visit_dates_of_data <-
  cbind(
    id_column,
    id_visit_date_column,
    bp_data_visit_dates_of_data
  )

```

```{r, create a frame of all columns with next observation carried backward - NOCB}
library(zoo)

bp_data_with_NOCB <-
  bp_data %>%
    group_by(id) %>% 
    mutate_all(
      funs(
        zoo::na.locf(
          ., 
          na.rm = FALSE, 
          fromLast=T))) #fromLast is what turns it into NOCB

#that gives us a whole frame of grouped next observation carried backward
```

```{r, create a frame of origin of NOCB data}
#we use the bp_data_visit_dates_of_data frame and perform NOCB on it, to have a frame that we can ally the NOCB data to
bp_data_visit_dates_of_NOCB <-
  bp_data_visit_dates_of_data %>%
    group_by(id) %>% 
    mutate_all(
      funs(
        zoo::na.locf(
          ., 
          na.rm = 
            FALSE, 
          fromLast=T ))) #fromLast is what turns it into NOCB

```

```{r, create a frame of all columns with last observation carried forward - LOCF}
bp_data_with_LOCF <-
  bp_data %>%
    group_by(id) %>% 
    mutate_all(
      funs(
        zoo::na.locf(
          ., 
          na.rm = FALSE, 
          fromLast=F))) #fromLast False keeps it as LOCF

#that gives us a whole frame of grouped last observation carried forward
```

```{r, create a frame of origin of LOCF data}
#we use the bp_data_visit_dates_of_data frame and perform LOCF on it, to have a frame that we can ally the LOCF data to
bp_data_visit_dates_of_LOCF <-
  bp_data_visit_dates_of_data %>%
    group_by(id) %>% 
    mutate_all(
      funs(zoo::na.locf(
        ., 
        na.rm = FALSE, 
        fromLast=F))) #fromLast False keeps it as LOCF

```

```{r, insert all columns with LOCF and NOCB and dates into the main frame for glucocorticoids}
#now we can just put the columns we want into the main frame

bp_data$GC_dose_1_LOCF_raw <-
  bp_data_with_LOCF$GC_dose_1

bp_data$GC_dose_1_LOCF_origin_date <-
  bp_data_visit_dates_of_LOCF$GC_dose_1

bp_data$GC_dose_1_NOCB_raw <-
  bp_data_with_NOCB$GC_dose_1

bp_data$GC_dose_1_NOCB_origin_date <-
  bp_data_visit_dates_of_NOCB$GC_dose_1
```

```{r, check my results of last observation carried forward and backward}
check_LOCF_for_GC <-
  bp_data[,c("id",
             "visit_date",
             "GC_dose_1",
             "GC_dose_1_LOCF_raw",
             "GC_dose_1_LOCF_origin_date",
             "GC_dose_1_NOCB_raw",
             "GC_dose_1_NOCB_origin_date"
             )]

write.csv(check_LOCF_for_GC, "check_LOCF_for_GC.csv")
```

```{r, create a function that adds each of the necessary columns to the main frame}
#name the function and tell it what to do
use_LOCF_and_NOCB_with_limits <- 
  function(name_of_column){

#to make this function more universal you would want to name all of the frames you enter into it. This would not only be bp_data, but also bp_data_with_LOCF etc. Or you could get it to carry forward and backward all dates within the same function. Keeping it all separate and named above makes it slightly more granular  
  
#test columns here to tweak the function:    
#name_of_column <- 
#  "absolute_total_daily_hydrocortisone_at_visit"
#name_of_column <-     "daily_preparation_of_GC_to_use"
column_from_LOCF_raw <- 
  bp_data_with_LOCF[,name_of_column]
names(column_from_LOCF_raw)[names(column_from_LOCF_raw)==name_of_column] <- 
  paste0("from_LOCF_raw")


column_from_LOCF_origin_date <- 
  bp_data_visit_dates_of_LOCF[,name_of_column]
names(column_from_LOCF_origin_date)[names(column_from_LOCF_origin_date)==name_of_column] <- 
  paste0("from_LOCF_origin_date")


visit_dates_LOCF <-
  data.frame(
    visit_date=bp_data$visit_date,
    visit_date_of_LOCF=as.vector(bp_data_visit_dates_of_LOCF[,name_of_column]))
#the problem is, the name of the column gets retained, so we force that into a standard name
names(visit_dates_LOCF)[2] <- "visit_date_of_LOCF" 

visit_dates_LOCF$years_from_LOCF <-
  as.numeric(
    difftime(
      visit_dates_LOCF$visit_date, 
      visit_dates_LOCF$visit_date_of_LOCF, 
      units="days"))/365.25

#then we pull out just the calculated column we care about
column_years_from_LOCF <-
  data.frame(
    to_rename = visit_dates_LOCF$years_from_LOCF)

names(column_years_from_LOCF)[names(column_years_from_LOCF)=="to_rename"] <- 
  paste0("years_from_LOCF")

column_from_NOCB_raw <- 
  bp_data_with_NOCB[,name_of_column]

names(column_from_NOCB_raw)[names(column_from_NOCB_raw)==name_of_column] <- 
  paste0("from_NOCB_raw")

column_from_NOCB_origin_date <- 
  bp_data_visit_dates_of_NOCB[,name_of_column]

names(column_from_NOCB_origin_date)[names(column_from_NOCB_origin_date)==name_of_column] <- 
  paste0("from_NOCB_origin_date")

visit_dates_NOCB <-
  data.frame(
    visit_date=bp_data$visit_date,
    visit_date_of_NOCB=as.vector(bp_data_visit_dates_of_NOCB[,name_of_column]))

#the problem is, the name of the column gets retained, so we force that into a standard name
names(visit_dates_NOCB)[2] <- "visit_date_of_NOCB" 

#remember when we calculate years from NOCB, the difference is the other way around
visit_dates_NOCB$years_from_NOCB <-
  as.numeric(difftime(visit_dates_NOCB$visit_date_of_NOCB, 
                      visit_dates_NOCB$visit_date, 
                      units="days"))/365.25

#then we pull out just the calculated column we care about
column_years_from_NOCB <-
  data.frame(to_rename = visit_dates_NOCB$years_from_NOCB)

names(column_years_from_NOCB)[names(column_years_from_NOCB)=="to_rename"] <- 
  paste0("years_from_NOCB")

calculated_frame <-
  cbind(
    bp_data[,"id"],
    bp_data[,"age_to_use"],
    bp_data[,"visit_date"],
    bp_data[,"maximum_years_LOCF"],
    bp_data[,"maximum_years_NOCB"],
    bp_data[,name_of_column],
    column_from_LOCF_raw,
    column_from_LOCF_origin_date,
    column_years_from_LOCF,
    column_from_NOCB_raw,
    column_from_NOCB_origin_date,
    column_years_from_NOCB
  )


#then we can create a column to use by assessing the column_years_from_LOCF against bp_data$maximum_years_LOCF
calculated_frame$column_to_use <-
  ifelse(calculated_frame$years_from_LOCF <= calculated_frame$maximum_years_LOCF,
         calculated_frame$from_LOCF_raw,
         NA)

#then we can alter the column to use IF IT IS CURRENTLY EMPTY by assessing the column_years_from_NOCB against bp_data$maximum_years_NOCB
calculated_frame$column_to_use <-
  ifelse(is.na(calculated_frame$column_to_use) &
         calculated_frame$years_from_NOCB <= calculated_frame$maximum_years_NOCB,
         calculated_frame$from_NOCB_raw,
         calculated_frame$column_to_use)

#create a directory where we show all the columns we've done this to
dir.create("locf_and_nocb_calculation_frames", showWarnings = FALSE)

write.csv(calculated_frame, 
          paste0("locf_and_nocb_calculation_frames/", 
                 name_of_column, 
                 "_calculated_frame.csv"),
          row.names = F)

sink(paste0("locf_and_nocb_calculation_frames/", 
                 name_of_column, 
                 "_missing_description.txt"))

print("This file will display descriptions of the original and imputed data if it is numeric. If a character column, it will display frequencies:")

if (is.numeric(calculated_frame$column_to_use)){
  print("Name of columne is : ")
  print(name_of_column)
  print("Description of original data:")
  print(descr(calculated_frame[,name_of_column]))
  print("Description of data using hierarchical LOCF and NOCB:")
  print(descr(calculated_frame$column_to_use))
}

if (is.character(calculated_frame$column_to_use)){
  print("Name of columne is : ")
  print(name_of_column)
  print("Description of original data:")
  print(freq(calculated_frame[,name_of_column]))
  print("Description of data using hierarchical LOCF and NOCB:")
  print(freq(calculated_frame$column_to_use))
}

sink()

#then we pull out just the carried forward number to use
carry_frame_to_join <-
  data.frame(
    id_visit_date=bp_data$id_visit_date,
    column_to_use=calculated_frame$column_to_use
  )

#now we have something to join we can rename the column of interest
names(carry_frame_to_join)[names(carry_frame_to_join)=="column_to_use"] <- 
  paste0(name_of_column, "_carried_to_use")

#then right at the end of the function we add it into our frame
bp_data_with_column <-
  left_join(bp_data, 
            carry_frame_to_join, 
            by="id_visit_date")



#assign our version with the column to bp_data within the global environment
assign(x="bp_data", 
       value=bp_data_with_column, 
       env=.GlobalEnv)

}


```

```{r, apply LOCF and NOCB function to glucocorticoid columns}
#apply to hydrocortisone
use_LOCF_and_NOCB_with_limits("daily_preparation_of_GC_to_use") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("total_daily_hydrocortisone_equivalent_at_visit") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("absolute_total_daily_hydrocortisone_at_visit") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("absolute_total_daily_prednisolone_at_visit") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("absolute_total_daily_prednisone_at_visit") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("absolute_total_daily_dexamethasone_at_visit") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("absolute_total_daily_cortisone_acetate_at_visit") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("absolute_daily_GC_dose_sum") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("Glucocorticoids...Current.Medication") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("Fludrocortisone...Current.Medication") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below

use_LOCF_and_NOCB_with_limits("Salt.replacement...Current.Medication") #note if you add any columns to add here, you also have to add manual corrections to when you don't want them carried below


```

```{r, correct inappropriate carry forwards of Not known for glucocorticoids - do this for all patients}
#if a patient has actively declared 'Not known' for whether they are taking GC, then they shouldn't have dose information
#before we do a blanket correction here, we should record how many this applies to 
print("This is the number of not knowns we have registered in the file. If it is registered as not known, we have to give it up and lose it from the data. ")
freq(bp_data$Glucocorticoids...Current.Medication_carried_to_use)

bp_data_GC_not_known <-
  subset(bp_data, Glucocorticoids...Current.Medication_carried_to_use=="Not known")

bp_data_patients_GC_not_known  <-
  subset(bp_data, id %in% bp_data_GC_not_known$id)[,c(
    "id",
    "id_visit_date",
    "Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..",
    "total_daily_fludro_dose",
    "converted_salt_mass",
    "Glucocorticoids...Current.Medication_original",
    "Glucocorticoids...Current.Medication",
    "Glucocorticoids...Current.Medication_carried_to_use",
    "Glucocorticoids.note...Current.Medication",
    "total_daily_hydrocortisone_equivalent_at_visit_carried_to_use",
    "absolute_daily_GC_dose_sum",
    "daily_preparation_of_GC_to_use",
    "total_daily_hydrocortisone_equivalent_at_visit",
    "Daily.adherence.to.therapy...Current.Medication",
    "Has.treatment.changed.since.last.visit...Current.Medication",
    "Why.was.treatment.changed...Current.Medication",
    "medicine_1",
    "GC_dose_1",
    "meds_unit_1")]

write.csv(bp_data_patients_GC_not_known, "bp_data_GC_not_known.csv")

  bp_data$daily_preparation_of_GC_to_use_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$daily_preparation_of_GC_to_use_carried_to_use)
  
  bp_data$total_daily_hydrocortisone_equivalent_at_visit_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$total_daily_hydrocortisone_equivalent_at_visit_carried_to_use)
  
  bp_data$absolute_total_daily_hydrocortisone_at_visit_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$absolute_total_daily_hydrocortisone_at_visit_carried_to_use)
  
  bp_data$absolute_total_daily_prednisolone_at_visit_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$absolute_total_daily_prednisolone_at_visit_carried_to_use)
  
  bp_data$absolute_total_daily_prednisone_at_visit_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$absolute_total_daily_prednisone_at_visit_carried_to_use)
  
  bp_data$absolute_total_daily_dexamethasone_at_visit_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$absolute_total_daily_dexamethasone_at_visit_carried_to_use)
  
  bp_data$absolute_total_daily_cortisone_acetate_at_visit_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$absolute_total_daily_cortisone_acetate_at_visit_carried_to_use)
  
  bp_data$absolute_total_daily_hydrocortisone_at_visit_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$absolute_total_daily_hydrocortisone_at_visit_carried_to_use)
  
  bp_data$absolute_daily_GC_dose_sum_carried_to_use <-
    ifelse(bp_data$Glucocorticoids...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$absolute_daily_GC_dose_sum_carried_to_use)



```


```{r, apply LOCF and NOCB to fludrocortisone column with zero}
#apply to fludrocortisone
use_LOCF_and_NOCB_with_limits("total_daily_fludro_dose_with_zero")
```

```{r, correct inappropriate carry forwards of Not known for fludrocortisone again now we have carried forward as we have extra data from the possible correction column to use}
bp_data$total_daily_fludro_dose_with_zero_carried_to_use <-
    ifelse(bp_data$Fludrocortisone...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$total_daily_fludro_dose_with_zero_carried_to_use)
```

```{r, create a check frame of fludrocortisone}
check_LOCF_for_fludrocortisone <-
  bp_data[,c("id",
             "visit_date",
             "age_to_use",
             "Fludrocortisone...Current.Medication_carried_to_use",
             "total_daily_fludro_dose",
             "total_daily_fludro_dose_with_zero_carried_to_use"
             )]

check_LOCF_for_fludrocortisone_with_no <-
  subset(check_LOCF_for_fludrocortisone,
         Fludrocortisone...Current.Medication_carried_to_use=="No")
descr(check_LOCF_for_fludrocortisone_with_no$total_daily_fludro_dose_with_zero_carried_to_use)
```

Now that we have zero doses of salt and corrections made for No and Not Known, we can carry forward

```{r, apply LOCF and NOCB to salts columns that have the mass of salt and whether they will later need correcting for weight}
#we now apply LOCF and NOCB to salt also
use_LOCF_and_NOCB_with_limits("converted_salt_mass_with_zero")
use_LOCF_and_NOCB_with_limits("converted_salt_per_kg_or_absolute")
```

We also then want to recorrect our converted_salt_mass_with_zero_carried_to_use column for whether they were not known or zero in the informative column that has been carried to use, because the informative column used above was the original column to keep the original data integrity for comparison of imputed versus non imputed data

```{r, correct inappropriate doses of Not known for salt using the carried to use column - do this for all patients}
bp_data$converted_salt_mass_with_zero_carried_to_use <-
    ifelse(bp_data$Salt.replacement...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$converted_salt_mass_with_zero_carried_to_use)
  
  bp_data$converted_salt_per_kg_or_absolute_carried_to_use <-
    ifelse(bp_data$Salt.replacement...Current.Medication_carried_to_use=="Not known",
           NA,
           bp_data$converted_salt_per_kg_or_absolute_carried_to_use)
```

```{r, correct inappropriate doses of No for salt using the carried to use column}
bp_data$converted_salt_mass_with_zero_carried_to_use <-
  ifelse(bp_data$Salt.replacement...Current.Medication_carried_to_use=="No", 
  0, 
  bp_data$converted_salt_mass_with_zero)
```






frequencies that helped assess:

```{r, accounting for zero entries for fludrocortisone}
freq(bp_data$visit_in_fludro_data)

freq(bp_data$ever_taken_fludro)
     
freq(bp_data$total_daily_fludro_dose_with_zero)

freq(bp_data$total_daily_fludro_dose_with_zero_carried_to_use)

freq(bp_data$Fludrocortisone...Current.Medication_carried_to_use)

print("Note the following columns from the longitudinal data:")
as.data.frame(freq(bp_data$Fludrocortisone.frequency...Current.Medication))

print("Whereas this comes from the fludrocortisone data frame:")
as.data.frame(freq(bp_data$fludrocortisone_frequency_number))
```

```{r, check consistency between Fludrocortisone...Current.Medication_carried_to_use and reported dosing of fludro}
print("Description of fludrocortisone treatmnet:")
freq(bp_data$Fludrocortisone...Current.Medication_carried_to_use)
print("Description of fludrocortisone dose:")
descr(bp_data$fludrocortisone_dose)
print("Description of fludrocortisone frequency:")
descr(bp_data$fludrocortisone_frequency_number)
print("Description of fludrocortisone frequency:")
freq(bp_data$Fludrocortisone.frequency...Current.Medication)

bp_data$fludro_dose_but_registry_not_taking <-
  ifelse(bp_data$Fludrocortisone...Current.Medication_carried_to_use=="No" &
           bp_data$fludrocortisone_dose>0,
         1,
         0)

freq(bp_data$fludro_dose_but_registry_not_taking )


#do the same for not known
bp_data$fludro_dose_but_registry_taking_not_known <-
  ifelse(bp_data$Fludrocortisone...Current.Medication_carried_to_use=="Not known" &
           bp_data$fludrocortisone_dose>0,
         1,
         0)
freq(bp_data$fludro_dose_but_registry_taking_not_known )
print("Therefore no discrepancy with those classed as 'Not Known'")
```

```{r, assess number of entries with Fludrocortisone...Current.Medication_carried_to_use and Fludrocortisone.frequency...Current.Medication is NA}
bp_data$fludro_registry_taking_but_frequency_not_known <-
  ifelse(bp_data$Fludrocortisone...Current.Medication_carried_to_use=="Yes" &
           is.na(bp_data$Fludrocortisone.frequency...Current.Medication) |
           bp_data$Fludrocortisone...Current.Medication_carried_to_use=="Yes" &
           is.na(bp_data$Fludrocortisone.frequency...Current.Medication) |
           bp_data$Fludrocortisone...Current.Medication_carried_to_use=="Yes" &
           is.na(bp_data$Fludrocortisone.frequency...Current.Medication),
         1,
         0)

freq(bp_data$fludro_registry_taking_but_frequency_not_known)
```



```{r, overall description of doses after carry forward and backward}
descr(bp_data$total_daily_hydrocortisone_equivalent_at_visit)
descr(bp_data$total_daily_fludro_dose_with_zero)
descr(bp_data$converted_salt_mass_with_zero)
freq(bp_data$Salt.replacement...Current.Medication_carried_to_use)
```

```{r, check what weve done with salt as intuitively we will expect more data in converted_salt_mass_with_zero_carried_to_use than in converted_salt_mass_with_zero}
cat("There should be more data in:")
descr(bp_data$converted_salt_mass_with_zero_carried_to_use)
cat("Than there is in this:")
descr(bp_data$converted_salt_mass_with_zero)
```


```{r, check what weve done with fludro as intuitively we will expect more data in total_daily_fludro_dose_with_zero_carried_to_use than in total_daily_fludro_dose_with_zero}
cat("There should be more data in:")
descr(bp_data$total_daily_fludro_dose_with_zero_carried_to_use)
cat("Than there is in this:")
descr(bp_data$total_daily_fludro_dose_with_zero)
```

```{r, end of file so save all the listed dataframes into the parent directory}
save_bp_files_function(
  parent_directory=location_of_data_files,
  parent_file="file_15")

Sys.time()
```

